---
title: "Examination of the value of eco-labeled products"
output: word_document
---

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(BEST)   # for Bayesian t tests
library(BANOVA)  # Bayesian ANOVAs
```

Categorical comparisons – product (with eco-label attribute) vs price

```{r get_data, echo=FALSE, include=FALSE}
col.def <- cols("YEAR" = col_integer(),
                "MONTH" = col_integer(),
                "DAY" = col_integer(),
                "DATE" = col_date(format = "%m/%d/%y"),
                "ZIP" = col_integer(),
                "LATITUDE" = col_double(),
                "LONGITUDE" = col_double(),
                "MKT_NAME" = col_character(),
                "MARKETNAME" = col_integer(),
                "MARKETTYPE" = col_integer(),
                "FULL_LABEL" = col_character(),
                "COMMON_NAME" = col_character(),
                "LENGTH_CM" = col_double(),
                "FOODGRP" = col_character(),
                "SPP_GROUP" = col_character(),
                "DSPPGRP" = col_integer(),
                "SPECIES" = col_character(),
                "FAMILY" = col_character(),
                "TL" = col_double(),
                "K_YR" = col_double(),
                "PRICE" = col_double(),
                "DCOUNTRY" = col_integer(),
                "COUNTRY" = col_character(),
                "DCONDITION" = col_integer(),
                "CONDITION" = col_character(),
                "PRODUCT_TYPE" = col_character(),
                "BRAND_NAME" = col_character(),
                "PROD_METHOD" = col_integer(),
                "KEYWORD" = col_character(),
                "ECOLABEL" = col_character(),
                "SFW_RATING" = col_integer(),
                "WILD" = col_integer(),
                "FARMED" = col_integer(),
                "FRESH" = col_integer(),
                "HVINVERT" = col_integer(),
                "SHRIMP" = col_integer(),
                "LOCAL" = col_integer(),
                "LIVE" = col_integer(),
                "SUSHI" = col_integer(),
                "RESPONSIBLE" = col_integer(),
                "MSC" = col_integer(),
                "SUSTAINABLE" = col_integer(),
                "MBA" = col_integer(),
                "MBA_CARD" = col_integer(),
                "MBA_APP" = col_integer(),
                "BAP" = col_integer(),
                "DBAPSTARS" = col_integer(),
                "BAP_LEVEL" = col_character(),
                "REGION" = col_character(),
                "GEAR" = col_character(),
                "SIZE_CLASS" = col_character(),
                "SHRIMP_PROCESSING" = col_character(),
                "DPROCCOUNTRY" = col_integer(),
                "PROCESSING_COUNTRY" = col_character(),
                "HACCP" = col_integer(),
                "SIZE_GROUP" = col_character(),
                "DOLPHIN_SAFE" = col_character(),
                "OTHER_TEXT" = col_character(),
                "GF" = col_character(),
                "O3" = col_character(),
                "NONGMO" = col_integer(),
                "SUSTAIN-" = col_integer(),
                "TRAC-" = col_integer(),
                "USA STATE" = col_character())

main.data <- read_csv(file = "data/SDSEAFOOD_Master_02042019_2.csv",
                      col_types = col.def)

# Bring in the keys:
key_country <- read.csv(file = "data/SDSEAFOOD_KEY_DCOUNTRY_02012019_1.csv")
key_condition <- read.csv(file = "data/SDSEAFOOD_KEY_DCONDITION_02012019_1.csv")
key_food.grp <- read.csv(file = "data/SDSEAFOOD_KEY_DFOODGRP_02012019_1.csv")
key_market.name <- read.csv(file = "data/SDSEAFOOD_KEY_DMARKETNAME_02012019_1.csv")
key_market.type <- read.csv(file = "data/SDSEAFOOD_KEY_DMARKETTYPE_02012019_1.csv")
key_MBA <- read.csv(file = "data/SDSEAFOOD_KEY_DMBA_X_02012019_1.csv")
key_spp.grp <- read.csv(file = "data/SDSEAFOOD_KEY_DSPPGRP_02012019_1.csv")

```


# 1.	What is the average price of eco-labeled seafood vs non-ecolabeled seafood of the same species?
	Filter by: 

## A.	Monterey Bay Aquarium (MBA) Green/Yellow (fresh products only; this is the Whole Foods “effect”)
Should I take out products with other ecolabels? 

### MBA
```{r get_MBA, echo=FALSE, include=FALSE}
# then filter away!
main.data %>% select(DATE, ZIP, LATITUDE, LONGITUDE, MKT_NAME,
         SPP_GROUP, DSPPGRP, PRICE, COUNTRY, DCONDITION,
         MBA, MSC, BAP) %>%
  filter(DCONDITION == 2)  %>%  # Fresh only
  filter(is.na(MSC))  %>% # remove MSC certified
  filter(is.na(BAP))  %>% # remove BAP certified
  mutate(MBA_1_2 = ifelse(is.na(MBA), 2, 
                          ifelse((MBA == 1 | MBA == 2), 1, 2))) %>%
  left_join(key_spp.grp, by = "DSPPGRP") -> MBA.data

# find which levels are available as pairs:
MBA.data %>% group_by(as.factor(DSPPGRP)) %>% 
  filter(MBA_1_2 == 1) %>%
  summarize(n = n()) -> MBA_1.summary

MBA.data %>% group_by(as.factor(DSPPGRP)) %>% 
  filter(MBA_1_2 == 2) %>%
  summarize(n = n()) -> MBA_2.summary

common.levels <- intersect(unique(MBA_1.summary$`as.factor(DSPPGRP)`),
                           unique(MBA_2.summary$`as.factor(DSPPGRP)`))

MBA.data <- MBA.data[MBA.data$DSPPGRP %in% common.levels,]

# MBA.data %>% group_by(as.factor(MBA_1_2), DSPPGRP) %>%
#   summarize(n = n()) -> MBA.summary


```

Interesting to note that variability for MBA 1 & 2 is less than that for others. We may compare that statistically but it's pretty obvious...

Doing Bayesian "t-tests" for these groups independently:
```{r MBA_tests, echo=FALSE, include=FALSE, cache=TRUE}

if (!file.exists("RData/MBA_test_results.rds")){
  BESTout <- vector(mode = "list", length = length(common.levels))
  k <- 1
  for (k in 1:length(common.levels)){
    MBA.data %>% filter(DSPPGRP == as.numeric(common.levels[k])) %>%
      select(MBA_1_2, PRICE) -> tmp
    
    tmp %>% filter(MBA_1_2 == 1) %>% 
      pull(PRICE) -> y1
    
    tmp %>% filter(MBA_1_2 == 2) %>% 
      pull(PRICE) -> y2
    
    if (var(y1) > 0 & var(y2) > 0 & !is.na(var(y1)) & !is.na(var(y2))){
      BESTout[[k]] <- BESTmcmc(y1, y2,
                               numSavedSteps = 10000,
                               burnInSteps = 5000,
                               thinSteps = 5,
                               parallel = TRUE)
      
    }
  }
  
  saveRDS(BESTout, "RData/MBA_test_results.rds")
  
} else {
  BESTout <- readRDS("RData/MBA_test_results.rds")
}

p.dif.gt.0 <- unlist(lapply(BESTout, 
                            FUN = function(x) {return(ifelse(!is.null(x), 
                                                             summary(x)["muDiff", "%>compVal"], 
                                                             NA))})) * 0.01

p.dif.gt.0.df <- data.frame(DSPPGRP = common.levels,
                            p = p.dif.gt.0)
```

 

```{r plot_MBA, echo=FALSE, fig.cap="Values on top indicate the probability that the means are different for each group."}

ggplot(MBA.data) +
  geom_boxplot(aes(x = as.factor(DSPPGRP), 
                   y = (PRICE), 
                   color = as.factor(MBA_1_2)))+
  scale_color_discrete(labels = c("MBA 1&2", "Others")) + 
  guides(color = guide_legend(title = NULL)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, 
                                   hjust = 1, size = 12)) +
  labs(x = "DSPPGRP", title = "MBA 1&2, Fresh products only") +
  geom_text(data = p.dif.gt.0.df,
            aes(x = as.factor(DSPPGRP), 
                y = max(MBA.data$PRICE), 
                label = signif(p, 2)))

```

## B.	Marine Stewardship Council (MSC) certification
```{r MSC_data, echo=FALSE, include=FALSE}

main.data %>% select(DATE, ZIP, LATITUDE, LONGITUDE, MKT_NAME,
         SPP_GROUP, DSPPGRP, PRICE, COUNTRY, DCONDITION,
         MBA, MSC, BAP) %>%
  filter(is.na(MBA)) %>%
  filter(is.na(BAP)) %>%
  mutate(MSC_1 = ifelse(is.na(MSC), 2, 1)) %>%
  left_join(key_spp.grp, by = "DSPPGRP") -> MSC.data

# find which levels are available as pairs:
MSC.data %>% group_by(as.factor(DSPPGRP)) %>% 
  filter(MSC_1 == 1) %>%
  summarize(n = n()) -> MSC_1.summary

MSC.data %>% group_by(as.factor(DSPPGRP)) %>% 
  filter(MSC_1 == 2) %>%
  summarize(n = n()) -> MSC_2.summary

common.levels <- intersect(unique(MSC_1.summary$`as.factor(DSPPGRP)`),
                           unique(MSC_2.summary$`as.factor(DSPPGRP)`))

MSC.data <- MSC.data[MSC.data$DSPPGRP %in% common.levels,]

```


Doing Bayesian "t-tests" for these groups independently:
```{r MSC_tests, echo=FALSE, include=FALSE, cache=TRUE}

if (!file.exists("RData/MSC_test_results.rds")){

  BESTout.MSC <- vector(mode = "list", length = length(common.levels))
  
  k <- 1
  for (k in 1:length(common.levels)){
    MSC.data %>% filter(DSPPGRP == as.numeric(common.levels[k])) %>%
      select(MSC_1, PRICE) -> tmp
    
    tmp %>% filter(MSC_1 == 1) %>% 
      pull(PRICE) -> y1
    
    tmp %>% filter(MSC_1 == 2) %>% 
      pull(PRICE) -> y2
    
    if (var(y1) > 0 & var(y2) > 0 & !is.na(var(y1)) & !is.na(var(y2))){
      BESTout.MSC[[k]] <- BESTmcmc(y1, y2,
                                   numSavedSteps = 10000,
                                   burnInSteps = 5000,
                                   thinSteps = 5,
                                   parallel = TRUE)
      
    }
  }
  saveRDS(BESTout.MSC, "RData/MSC_test_results.rds")
} else {
  BESTout.MSC <- readRDS("RData/MSC_test_results.rds")
  
}  

p.dif.gt.0 <- unlist(lapply(BESTout.MSC, 
                            FUN = function(x) {return(ifelse(!is.null(x), 
                                                             summary(x)["muDiff", "%>compVal"], 
                                                             NA))})) * 0.01

p.dif.gt.0.df <- data.frame(DSPPGRP = common.levels,
                            p = p.dif.gt.0)
```

```{r}
ggplot(MSC.data) +
  geom_boxplot(aes(x = as.factor(DSPPGRP), 
                   y = (PRICE), color = as.factor(MSC_1)))+
  scale_color_discrete(labels = c("MSC", "Others")) + 
  guides(color = guide_legend(title = NULL)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, 
                                   hjust = 1, size = 12)) +
  labs(x = "DSPPGRP", main = "MSC")+ 
  geom_text(data = p.dif.gt.0.df,
            aes(x = as.factor(DSPPGRP), 
                y = max(MSC.data$PRICE), 
                label = signif(p, 2)))
```


### Fresh; frozen; shelf stable products run separately 
#### Fresh
```{r}
MSC.data %>% 
  filter(DCONDITION == 2) %>% 
  filter(is.na(MBA)) %>%
  filter(is.na(BAP)) -> MSC.fresh.data


# find which levels are available as pairs:
MSC.fresh.data %>% group_by(as.factor(DSPPGRP)) %>% 
  filter(MSC_1 == 1) %>%
  summarize(n = n()) -> MSC.fresh_1.summary

MSC.fresh.data %>% group_by(as.factor(DSPPGRP)) %>% 
  filter(MSC_1 == 2) %>%
  summarize(n = n()) -> MSC.fresh_2.summary

common.levels <- intersect(unique(MSC.fresh_1.summary$`as.factor(DSPPGRP)`),
                           unique(MSC.fresh_2.summary$`as.factor(DSPPGRP)`))

MSC.fresh.data <- MSC.fresh.data[MSC.fresh.data$DSPPGRP %in% common.levels,]


```


Doing Bayesian "t-tests" for these groups independently:
```{r MSC_tests_fresh, echo=FALSE, include=FALSE, cache=TRUE}

if (!file.exists("RData/MSC_fresh_test_results.rds")){

  BESTout.MSC.fresh <- vector(mode = "list", length = length(common.levels))
  k <- 1
  for (k in 1:length(common.levels)){
    MSC.fresh.data %>% filter(DSPPGRP == as.numeric(common.levels[k])) %>%
      select(MSC_1, PRICE) -> tmp
    
    tmp %>% filter(MSC_1 == 1) %>% 
      pull(PRICE) -> y1
    
    tmp %>% filter(MSC_1 == 2) %>% 
      pull(PRICE) -> y2
    
    if (var(y1) > 0 & var(y2) > 0 & !is.na(var(y1)) & !is.na(var(y2))){
      BESTout.MSC.fresh[[k]] <- BESTmcmc(y1, y2,
                                         numSavedSteps = 10000,
                                         burnInSteps = 5000,
                                         thinSteps = 5,
                                         parallel = TRUE)
      
    }
  }
  
  saveRDS(BESTout.MSC.fresh, "RData/MSC_fresh_test_results.rds")
} else {
  BESTout.MSC.fresh <- readRDS("RData/MSC_fresh_test_results.rds")
}

p.dif.gt.0 <- unlist(lapply(BESTout.MSC.fresh, 
                            FUN = function(x) {return(ifelse(!is.null(x), 
                                                             summary(x)["muDiff", "%>compVal"], 
                                                             NA))})) * 0.01

p.dif.gt.0.df <- data.frame(DSPPGRP = common.levels,
                            p = p.dif.gt.0)
```

```{r}
ggplot(MSC.fresh.data) +
  geom_boxplot(aes(x = as.factor(DSPPGRP), 
                   y = (PRICE), color = as.factor(MSC_1)))+
  scale_color_discrete(labels = c("MSC", "Others")) + 
  guides(color = guide_legend(title = NULL)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, 
                                   hjust = 1, size = 12)) +
  labs(x = "DSPPGRP", title = "Fresh") + 
  geom_text(data = p.dif.gt.0.df,
            aes(x = as.factor(DSPPGRP), 
                y = max(MSC.fresh.data$PRICE), 
                label = signif(p, 2)))

```


#### Frozen

```{r MSC_frozen, echo=FALSE}
MSC.data %>% 
  filter(DCONDITION == 5 | DCONDITION == 6) %>% 
  filter(is.na(MBA)) %>%
  filter(is.na(BAP)) -> MSC.frozen.data

# find which levels are available as pairs:
MSC.frozen.data %>% group_by(as.factor(DSPPGRP)) %>% 
  filter(MSC_1 == 1) %>%
  summarize(n = n()) -> MSC.frozen_1.summary

MSC.frozen.data %>% group_by(as.factor(DSPPGRP)) %>% 
  filter(MSC_1 == 2) %>%
  summarize(n = n()) -> MSC.frozen_2.summary

common.levels <- intersect(unique(MSC.frozen_1.summary$`as.factor(DSPPGRP)`),
                           unique(MSC.frozen_2.summary$`as.factor(DSPPGRP)`))

MSC.frozen.data <- MSC.frozen.data[MSC.frozen.data$DSPPGRP %in% common.levels,]


```

```{r MSC_tests_frozen, echo=FALSE, include=FALSE, cache=TRUE}

if (!file.exists("RData/MSC_frozen_test_results.rds")){

  BESTout.MSC.frozen <- vector(mode = "list", length = length(common.levels))
  k <- 1
  for (k in 1:length(common.levels)){
    MSC.frozen.data %>% filter(DSPPGRP == as.numeric(common.levels[k])) %>%
      select(MSC_1, PRICE) -> tmp
    
    tmp %>% filter(MSC_1 == 1) %>% 
      pull(PRICE) -> y1
    
    tmp %>% filter(MSC_1 == 2) %>% 
      pull(PRICE) -> y2
    
    if (var(y1) > 0 & var(y2) > 0 & !is.na(var(y1)) & !is.na(var(y2))){
      BESTout.MSC.frozen[[k]] <- BESTmcmc(y1, y2,
                                   numSavedSteps = 10000,
                                   burnInSteps = 5000,
                                   thinSteps = 5,
                                   parallel = TRUE)
      
    }
  }
  
  saveRDS(BESTout.MSC.frozen, "RData/MSC_frozen_test_results.rds")
} else {
  BESTout.MSC.frozen <- readRDS("RData/MSC_frozen_test_results.rds")
}

p.dif.gt.0 <- unlist(lapply(BESTout.MSC.frozen, 
                            FUN = function(x) {return(ifelse(!is.null(x), 
                                                             summary(x)["muDiff", "%>compVal"], 
                                                             NA))})) * 0.01

p.dif.gt.0.df <- data.frame(DSPPGRP = common.levels,
                            p = p.dif.gt.0)
```

```{r MSC_frozen_plot, echo=FALSE}
ggplot(MSC.frozen.data) +
  geom_boxplot(aes(x = as.factor(DSPPGRP), 
                   y = (PRICE), color = as.factor(MSC_1)))+
  scale_color_discrete(labels = c("MSC", "Others")) + 
  guides(color = guide_legend(title = NULL)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, 
                                   hjust = 1, size = 12)) +
  labs(x = "DSPPGRP", title = "Frozen") + 
  geom_text(data = p.dif.gt.0.df,
            aes(x = as.factor(DSPPGRP), 
                y = max(MSC.frozen.data$PRICE), 
                label = signif(p, 2)))
```



#### Shelf-stable
```{r MSC_ss, echo=FALSE}
MSC.data %>% 
  filter(DCONDITION == 7 | DCONDITION == 8) %>% 
  filter(is.na(MBA)) %>%
  filter(is.na(BAP)) -> MSC.SS.data

# find which levels are available as pairs:
MSC.SS.data %>% group_by(as.factor(DSPPGRP)) %>% 
  filter(MSC_1 == 1) %>%
  summarize(n = n()) -> MSC.SS_1.summary

MSC.SS.data %>% group_by(as.factor(DSPPGRP)) %>% 
  filter(MSC_1 == 2) %>%
  summarize(n = n()) -> MSC.SS_2.summary

common.levels <- intersect(unique(MSC.SS_1.summary$`as.factor(DSPPGRP)`),
                           unique(MSC.SS_2.summary$`as.factor(DSPPGRP)`))

MSC.SS.data <- MSC.SS.data[MSC.SS.data$DSPPGRP %in% common.levels,]

```


```{r MSC_tests_SS, echo=FALSE, include=FALSE, cache=TRUE}

if (!file.exists("RData/MSC_SS_test_results.rds")){

  BESTout.MSC.SS <- vector(mode = "list", length = length(common.levels))
  k <- 1
  for (k in 1:length(common.levels)){
    MSC.SS.data %>% filter(DSPPGRP == as.numeric(common.levels[k])) %>%
      select(MSC_1, PRICE) -> tmp
    
    tmp %>% filter(MSC_1 == 1) %>% 
      pull(PRICE) -> y1
    
    tmp %>% filter(MSC_1 == 2) %>% 
      pull(PRICE) -> y2
    
    if (var(y1) > 0 & var(y2) > 0 & !is.na(var(y1)) & !is.na(var(y2))){
      BESTout.MSC.SS[[k]] <- BESTmcmc(y1, y2,
                                   numSavedSteps = 10000,
                                   burnInSteps = 5000,
                                   thinSteps = 5,
                                   parallel = TRUE)
      
    
    }
  }
  
  saveRDS(BESTout.MSC.SS, "RData/MSC_SS_test_results.rds")
} else {
  BESTout.MSC.SS <- readRDS("RData/MSC_SS_test_results.rds")
}

p.dif.gt.0 <- unlist(lapply(BESTout.MSC.SS, 
                            FUN = function(x) {return(ifelse(!is.null(x), 
                                                             summary(x)["muDiff", "%>compVal"], 
                                                             NA))})) * 0.01

p.dif.gt.0.df <- data.frame(DSPPGRP = common.levels,
                            p = p.dif.gt.0)
```


```{r MSC_SS_plot, echo=FALSE}

ggplot(MSC.SS.data) +
  geom_boxplot(aes(x = as.factor(DSPPGRP), 
                   y = (PRICE), color = as.factor(MSC_1)))+
  scale_color_discrete(labels = c("MSC", "Others")) + 
  guides(color = guide_legend(title = NULL)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, 
                                   hjust = 1, size = 12)) +
  labs(x = "DSPPGRP", title = "Shelf-stable") + 
  geom_text(data = p.dif.gt.0.df,
            aes(x = as.factor(DSPPGRP), 
                y = max(MSC.SS.data$PRICE), 
                label = signif(p, 2)))

```


## C.	Best Aquaculture Practices (BAP)
	Identify the species that have these labels – if this isn’t straightforward, we will help
	Please compare average price/lb of the same species with and without these labels, within product type category (fresh w eco-label vs. fresh non-ecolabel, frozen w ecolabel vs. frozen without ecolabel, shelf stable w ecolabel vs. shelf stable without ecolabel)
```{r BAP_data, echo=FALSE, include=FALSE}

main.data %>% select(DATE, ZIP, LATITUDE, LONGITUDE, MKT_NAME,
         SPP_GROUP, DSPPGRP, PRICE, COUNTRY, DCONDITION,
         MBA, MSC, BAP) %>%
  filter(is.na(MBA)) %>%
  filter(is.na(MSC)) %>%
  mutate(BAP_1 = ifelse(is.na(BAP), 2, 1)) %>%
  left_join(key_spp.grp, by = "DSPPGRP") -> BAP.data

# find which levels are available as pairs:
BAP.data %>% group_by(as.factor(DSPPGRP)) %>% 
  filter(BAP_1 == 1) %>%
  summarize(n = n()) -> BAP_1.summary

BAP.data %>% group_by(as.factor(DSPPGRP)) %>% 
  filter(BAP_1 == 2) %>%
  summarize(n = n()) -> BAP_2.summary

common.levels <- intersect(unique(BAP_1.summary$`as.factor(DSPPGRP)`),
                           unique(BAP_2.summary$`as.factor(DSPPGRP)`))

BAP.data <- BAP.data[BAP.data$DSPPGRP %in% common.levels,]

```


### a.	Fresh

```{r BAP_fresh, echo=FALSE}
BAP.data %>% 
  filter(DCONDITION == 2) -> BAP.fresh.data

# find which levels are available as pairs:
BAP.fresh.data %>% group_by(as.factor(DSPPGRP)) %>% 
  filter(BAP_1 == 1) %>%
  summarize(n = n()) -> BAP.fresh_1.summary

BAP.fresh.data %>% group_by(as.factor(DSPPGRP)) %>% 
  filter(BAP_1 == 2) %>%
  summarize(n = n()) -> BAP.fresh_2.summary

common.levels <- intersect(unique(BAP.fresh_1.summary$`as.factor(DSPPGRP)`),
                           unique(BAP.fresh_2.summary$`as.factor(DSPPGRP)`))

BAP.fresh.data <- BAP.fresh.data[BAP.fresh.data$DSPPGRP %in% common.levels,]


```

There aren't enough sample sizes to do meaningful comparison here.  
Doing Bayesian "t-tests" for these groups independently:
```{r BAP_tests_fresh, echo=FALSE, include=FALSE, cache=TRUE}

if (!file.exists("RData/BAP_fresh_test_results.rds")){

  BESTout.BAP.fresh <- vector(mode = "list", length = length(common.levels))
  k <- 1
  for (k in 1:length(common.levels)){
    BAP.fresh.data %>% filter(DSPPGRP == as.numeric(common.levels[k])) %>%
      select(BAP_1, PRICE) -> tmp
    
    tmp %>% filter(BAP_1 == 1) %>% 
      pull(PRICE) -> y1
    
    tmp %>% filter(BAP_1 == 2) %>% 
      pull(PRICE) -> y2
    
    if (var(y1) > 0 & var(y2) > 0 & !is.na(var(y1)) & !is.na(var(y2))){
      BESTout.BAP.fresh[[k]] <- BESTmcmc(y1, y2,
                                         numSavedSteps = 10000,
                                         burnInSteps = 5000,
                                         thinSteps = 5,
                                         parallel = TRUE)
      
    }
  }
  
  saveRDS(BESTout.BAP.fresh, "RData/BAP_fresh_test_results.rds")
} else {
  BESTout.BAP.fresh <- readRDS("RData/BAP_fresh_test_results.rds")
}

p.dif.gt.0 <- unlist(lapply(BESTout.BAP.fresh, 
                            FUN = function(x) {return(ifelse(!is.null(x), 
                                                             summary(x)["muDiff", "%>compVal"], 
                                                             NA))})) * 0.01

p.dif.gt.0.df <- data.frame(DSPPGRP = common.levels,
                            p = p.dif.gt.0)
```

```{r}
ggplot(BAP.fresh.data) +
  geom_boxplot(aes(x = as.factor(DSPPGRP), 
                   y = (PRICE), color = as.factor(BAP_1)))+
  scale_color_discrete(labels = c("BAP", "Others")) + 
  guides(color = guide_legend(title = NULL)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, 
                                   hjust = 1, size = 12)) +
  labs(x = "DSPPGRP", title = "Fresh") + 
  geom_text(data = p.dif.gt.0.df,
            aes(x = as.factor(DSPPGRP), 
                y = max(MSC.fresh.data$PRICE), 
                label = signif(p, 2)))

```

### Frozen products	

```{r BAP_frozen, echo=FALSE}
BAP.data %>% 
  filter(DCONDITION == 5 | DCONDITION == 6) -> BAP.frozen.data

# find which levels are available as pairs:
BAP.frozen.data %>% group_by(as.factor(DSPPGRP)) %>% 
  filter(BAP_1 == 1) %>%
  summarize(n = n()) -> BAP.frozen_1.summary

BAP.frozen.data %>% group_by(as.factor(DSPPGRP)) %>% 
  filter(BAP_1 == 2) %>%
  summarize(n = n()) -> BAP.frozen_2.summary

common.levels <- intersect(unique(BAP.frozen_1.summary$`as.factor(DSPPGRP)`),
                           unique(BAP.frozen_2.summary$`as.factor(DSPPGRP)`))

BAP.frozen.data <- BAP.frozen.data[BAP.frozen.data$DSPPGRP %in% common.levels,]


```

```{r BAP_tests_frozen, echo=FALSE, include=FALSE, cache=TRUE}

if (!file.exists("RData/BAP_frozen_test_results.rds")){

  BESTout.BAP.frozen <- vector(mode = "list", length = length(common.levels))
  k <- 1
  for (k in 1:length(common.levels)){
    BAP.frozen.data %>% filter(DSPPGRP == as.numeric(common.levels[k])) %>%
      select(BAP_1, PRICE) -> tmp
    
    tmp %>% filter(BAP_1 == 1) %>% 
      pull(PRICE) -> y1
    
    tmp %>% filter(BAP_1 == 2) %>% 
      pull(PRICE) -> y2
    
    if (var(y1) > 0 & var(y2) > 0 & !is.na(var(y1)) & !is.na(var(y2))){
      BESTout.BAP.frozen[[k]] <- BESTmcmc(y1, y2,
                                          numSavedSteps = 10000,
                                          burnInSteps = 5000,
                                          thinSteps = 5,
                                          parallel = TRUE)
      
    }
  }
  
  saveRDS(BESTout.BAP.frozen, "RData/BAP_frozen_test_results.rds")
} else {
  BESTout.BAP.frozen <- readRDS("RData/BAP_frozen_test_results.rds")
}

p.dif.gt.0 <- unlist(lapply(BESTout.BAP.frozen, 
                            FUN = function(x) {return(ifelse(!is.null(x), 
                                                             summary(x)["muDiff", "%>compVal"], 
                                                             NA))})) * 0.01

p.dif.gt.0.df <- data.frame(DSPPGRP = common.levels,
                            p = p.dif.gt.0)
```

```{r}
ggplot(BAP.frozen.data) +
  geom_boxplot(aes(x = as.factor(DSPPGRP), 
                   y = (PRICE), color = as.factor(BAP_1)))+
  scale_color_discrete(labels = c("BAP", "Others")) + 
  guides(color = guide_legend(title = NULL)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, 
                                   hjust = 1, size = 12)) +
  labs(x = "DSPPGRP", title = "Frozen") + 
  geom_text(data = p.dif.gt.0.df,
            aes(x = as.factor(DSPPGRP), 
                y = max(BAP.frozen.data$PRICE), 
                label = signif(p, 2)))
```



#### Shelf-stable
None of SS products had BAP certificate.  

```{r BAP_ss_data, echo=FALSE}
BAP.data %>% 
  filter(DCONDITION == 7 | DCONDITION == 8) -> BAP.SS.data

# find which levels are available as pairs:
BAP.SS.data %>% group_by(as.factor(DSPPGRP)) %>% 
  filter(BAP_1 == 1) %>%
  summarize(n = n()) -> BAP.SS_1.summary

BAP.SS.data %>% group_by(as.factor(DSPPGRP)) %>% 
  filter(BAP_1 == 2) %>%
  summarize(n = n()) -> BAP.SS_2.summary

common.levels <- intersect(unique(BAP.SS_1.summary$`as.factor(DSPPGRP)`),
                           unique(BAP.SS_2.summary$`as.factor(DSPPGRP)`))

BAP.SS.data <- BAP.SS.data[BAP.SS.data$DSPPGRP %in% common.levels,]

```


```{r BAP_tests_SS, echo=FALSE, include=FALSE, cache=TRUE}

if (!file.exists("RData/BAP_SS_test_results.rds")){

  BESTout.BAP.SS <- vector(mode = "list", length = length(common.levels))
  k <- 1
  for (k in 1:length(common.levels)){
    BAP.SS.data %>% filter(DSPPGRP == as.numeric(common.levels[k])) %>%
      select(BAP_1, PRICE) -> tmp
    
    tmp %>% filter(BAP_1 == 1) %>% 
      pull(PRICE) -> y1
    
    tmp %>% filter(BAP_1 == 2) %>% 
      pull(PRICE) -> y2
    
    if (var(y1) > 0 & var(y2) > 0 & !is.na(var(y1)) & !is.na(var(y2))){
      BESTout.BAP.SS[[k]] <- BESTmcmc(y1, y2,
                                   numSavedSteps = 10000,
                                   burnInSteps = 5000,
                                   thinSteps = 5,
                                   parallel = TRUE)
      
    
    }
  }
  
  saveRDS(BESTout.BAP.SS, "RData/BAP_SS_test_results.rds")
} else {
  BESTout.BAP.SS <- readRDS("RData/BAP_SS_test_results.rds")
}

p.dif.gt.0 <- unlist(lapply(BESTout.BAP.SS, 
                            FUN = function(x) {return(ifelse(!is.null(x), 
                                                             summary(x)["muDiff", "%>compVal"], 
                                                             NA))})) * 0.01

p.dif.gt.0.df <- data.frame(DSPPGRP = common.levels,
                            p = p.dif.gt.0)
```


```{r BAP_SS_plot, echo=FALSE}

ggplot(BAP.SS.data) +
  geom_boxplot(aes(x = as.factor(DSPPGRP), 
                   y = (PRICE), color = as.factor(BAP_1)))+
  scale_color_discrete(labels = c("BAP", "Others")) + 
  guides(color = guide_legend(title = NULL)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, 
                                   hjust = 1, size = 12)) +
  labs(x = "DSPPGRP", title = "Shelf-stable") + 
  geom_text(data = p.dif.gt.0.df,
            aes(x = as.factor(DSPPGRP), 
                y = max(BAP.SS.data$PRICE), 
                label = signif(p, 2)))

```
	
# 2.	What is the price of eco-labeled shrimp vs non-ecolabeled shrimp? 
Filter by: 
## A.	MSC - tiny shrimp, P. jordani (these are size tiny, fresh, wild-caught US and Canada) 

```{r P_jordani_data, echo=FALSE}
main.data %>% select(DATE, ZIP, LATITUDE, LONGITUDE, MKT_NAME,
         SPP_GROUP, DSPPGRP, PRICE, COUNTRY, DCONDITION, SHRIMP,
         SPECIES, MBA, MSC, BAP) %>%
  filter(SPECIES == "Pandalus jordani") %>%
  mutate(MSC_1 = ifelse(is.na(MSC), 2, 1)) -> P.jordani.data

# find which levels are available as pairs:
P.jordani.data %>% 
  filter(MSC_1 == 1) %>%
  summarize(n = n()) -> MSC_P.jordani_1.summary

P.jordani.data %>% 
  filter(MSC_1 == 2) %>%
  summarize(n = n()) -> MSC_P.jordani_2.summary


```


```{r P_jordani_tests_MSC, echo=FALSE, include=FALSE, cache=TRUE}

if (!file.exists("RData/P_jordani_MSC_test_results.rds")){

    P.jordani.data %>% filter(MSC_1 == 1) %>% 
      pull(PRICE) -> y1
    
    P.jordani.data %>% filter(MSC_1 == 2) %>% 
      pull(PRICE) -> y2
    
    if (var(y1) > 0 & var(y2) > 0 & !is.na(var(y1)) & !is.na(var(y2))){
      BESTout.P.jordani <- BESTmcmc(y1, y2,
                                    numSavedSteps = 10000,
                                    burnInSteps = 5000,
                                    thinSteps = 5,
                                    parallel = TRUE)
      
      
    }
  saveRDS(BESTout.P.jordani, "RData/P_jordani_MSC_test_results.rds")
} else {
  BESTout.P.jordani <- readRDS("RData/P_jordani_MSC_test_results.rds")
}

p.dif.gt.0 <- summary(BESTout.P.jordani)["muDiff", "%>compVal"] * 0.01

p.dif.gt.0.df <- data.frame(p = p.dif.gt.0)
```


```{r P_jordani_tests_MSC_plot, echo=FALSE}

ggplot(P.jordani.data) +
  geom_boxplot(aes(x = as.factor(MSC_1), 
                   y = (PRICE))) +
  #scale_color_discrete(labels = c("BAP", "Others")) + 
  #guides(color = guide_legend(title = NULL)) +
  # theme(axis.text.x = element_text(angle = 90, vjust = 0.5, 
  #                                  hjust = 1, size = 12)) +
  scale_x_discrete(labels = c("MSC", "non-MSC")) +
  labs(x = "", title = "P. jordani") + 
  geom_text(data = p.dif.gt.0.df,
            aes(x = 1, 
                y = max(P.jordani.data$PRICE), 
                label = signif(p, 2)))

```



## B.	MBA - white shrimp. L. setiferus  (only one size; fresh, wild caught US & Canada)

```{r MBA_L_setiferus, echo=FALSE}
main.data %>% select(DATE, ZIP, LATITUDE, LONGITUDE, MKT_NAME,
         SPP_GROUP, DSPPGRP, PRICE, COUNTRY, DCONDITION, SHRIMP,
         SPECIES, MBA, MSC, BAP) %>%
  filter(SPECIES == "Litopenaeus setiferus") %>%
  filter(is.na(MSC))  %>% # remove MSC certified
  filter(is.na(BAP))  %>% # remove BAP certified
  mutate(MBA_1_2 = ifelse(is.na(MBA), 2, 
                          ifelse((MBA == 1 | MBA == 2), 1, 2)))  -> L.setiferus.data

# find which levels are available as pairs:
L.setiferus.data %>% 
  filter(MBA_1_2 == 1) %>%
  summarize(n = n()) -> MBA_L.setiferus_1.summary

L.setiferus.data %>% 
  filter(MBA_1_2 == 2) %>%
  summarize(n = n()) -> MBA_L.setiferus_2.summary


```


```{r MBA_L_setiferus_test, echo=FALSE, include=FALSE, cache=TRUE}

if (!file.exists("RData/L_setiferus_test_results.rds")){

    L.setiferus.data %>% filter(MBA_1_2 == 1) %>% 
      pull(PRICE) -> y1
    
    L.setiferus.data %>% filter(MBA_1_2 == 2) %>% 
      pull(PRICE) -> y2
    
    if (var(y1) > 0 & var(y2) > 0 & !is.na(var(y1)) & !is.na(var(y2))){
      BESTout.L.setiferus <- BESTmcmc(y1, y2,
                                    numSavedSteps = 10000,
                                    burnInSteps = 5000,
                                    thinSteps = 5,
                                    parallel = TRUE)
      
      
    }
  saveRDS(BESTout.L.setiferus, "RData/L_setiferus_test_results.rds")
} else {
  BESTout.L.setiferus <- readRDS("RData/L_setiferus_test_results.rds")
}

p.dif.gt.0 <- summary(BESTout.L.setiferus)["muDiff", "%>compVal"] * 0.01

p.dif.gt.0.df <- data.frame(p = p.dif.gt.0)
```


```{r L_setiferus_tests_MBA_plot, echo=FALSE}

ggplot(L.setiferus.data) +
  geom_boxplot(aes(x = as.factor(MBA_1_2), 
                   y = (PRICE))) +
  #scale_color_discrete(labels = c("BAP", "Others")) + 
  #guides(color = guide_legend(title = NULL)) +
  # theme(axis.text.x = element_text(angle = 90, vjust = 0.5, 
  #                                  hjust = 1, size = 12)) +
  scale_x_discrete(labels = c("MBA 1&2", "Other")) +
  labs(x = "", title = "L. setiferus") + 
  geom_text(data = p.dif.gt.0.df,
            aes(x = 1, 
                y = max(L.setiferus.data$PRICE), 
                label = signif(p, 2)))

```

## C.	Fair Trade – white and blue shrimp; not giant size; fresh, wild; Del Pacifico product
Northen white shrimp (*Litopenaeus setiferus*) and blue shrimp (*Litopenaeus stylirostris*). What is "Del Pacifico product"? 

```{r FairTrade_L_setiferus, echo=FALSE}
main.data %>% select(DATE, ZIP, LATITUDE, LONGITUDE, MKT_NAME,
         SPP_GROUP, DSPPGRP, PRICE, COUNTRY, DCONDITION, SHRIMP,
         SPECIES, ECOLABEL, MBA, MSC, BAP) %>%
  filter(SPECIES == "Litopenaeus setiferus" |
           SPECIES == "Litopenaeus stylirostris") %>%
  mutate(ECOLABEL_f = as.factor(ECOLABEL)) %>%
  filter(is.na(MSC))  %>% # remove MSC certified
  filter(is.na(BAP))  %>% # remove BAP certified
  mutate(EL_1 = ifelse(is.na(ECOLABEL_f), 2, 1)) -> L.setiferus.FairTrade.data

# find which levels are available as pairs:
L.setiferus.FairTrade.data %>% 
  filter(EL_1 == 1) %>%
  summarize(n = n()) ->L.setiferus.FairTrade_1.summary

L.setiferus.FairTrade.data %>% 
  filter(EL_1 == 2) %>%
  summarize(n = n()) -> L.setiferus.FairTrade_2.summary


```


```{r FairTrade_L_setiferus_FairTrade_test, echo=FALSE, include=FALSE, cache=TRUE}

if (!file.exists("RData/L_setiferus_FairTrade_test_results.rds")){

    L.setiferus.FairTrade.data %>% filter(EL_1 == 1) %>% 
      pull(PRICE) -> y1
    
    L.setiferus.FairTrade.data %>% filter(EL_1 == 2) %>% 
      pull(PRICE) -> y2
    
    if (var(y1) > 0 & var(y2) > 0 & !is.na(var(y1)) & !is.na(var(y2))){
      BESTout.L.setiferus.FairTrade <- BESTmcmc(y1, y2,
                                    numSavedSteps = 10000,
                                    burnInSteps = 5000,
                                    thinSteps = 5,
                                    parallel = TRUE)
      
      
    }
  saveRDS(BESTout.L.setiferus.FairTrade, "RData/L_setiferus_FairTrade_test_results.rds")
} else {
  BESTout.L.setiferus.FairTrade <- readRDS("RData/L_setiferus_FairTrade_test_results.rds")
}

p.dif.gt.0 <- summary(BESTout.L.setiferus.FairTrade)["muDiff", "%>compVal"] * 0.01

p.dif.gt.0.df <- data.frame(p = p.dif.gt.0)
```


```{r L_setiferus_tests_FairTrade_plot, echo=FALSE}

ggplot(L.setiferus.FairTrade.data) +
  geom_boxplot(aes(x = as.factor(EL_1), 
                   y = (PRICE))) +
  #scale_color_discrete(labels = c("BAP", "Others")) + 
  #guides(color = guide_legend(title = NULL)) +
  # theme(axis.text.x = element_text(angle = 90, vjust = 0.5, 
  #                                  hjust = 1, size = 12)) +
  scale_x_discrete(labels = c("Fair trade", "Other")) +
  labs(x = "", title = "L. setiferus") + 
  geom_text(data = p.dif.gt.0.df,
            aes(x = 1, 
                y = max(L.setiferus.FairTrade.data$PRICE), 
                label = signif(p, 2)))

```


## D.	BAP whiteleg shrimp (farmed)
```{r BAP_L_vannamei, echo=FALSE}
main.data %>% select(DATE, ZIP, LATITUDE, LONGITUDE, MKT_NAME,
         SPP_GROUP, DSPPGRP, PRICE, COUNTRY, DCONDITION, SHRIMP,
         SPECIES, MBA, MSC, BAP) %>%
  filter(SPECIES == "Litopenaeus vannamei") %>%
  filter(is.na(MSC))  %>% # remove MSC certified
  filter(is.na(MBA))  %>% # remove BAP certified
  mutate(BAP_1 = ifelse(is.na(BAP), 2, 1)) -> L.vannamei.BAP.data

# find which levels are available as pairs:
L.vannamei.BAP.data %>% 
  filter(BAP_1 == 1) %>%
  summarize(n = n()) ->L.vannamei.BAP_1.summary

L.vannamei.BAP.data %>% 
  filter(BAP_1 == 2) %>%
  summarize(n = n()) -> L.vannamei.BAP_2.summary


```


```{r BAP_L_vannamei_test, echo=FALSE, include=FALSE, cache=TRUE}

if (!file.exists("RData/L_vannamei_BAP_test_results.rds")){

    L.vannamei.BAP.data %>% filter(BAP_1 == 1) %>% 
      pull(PRICE) -> y1
    
    L.vannamei.BAP.data %>% filter(BAP_1 == 2) %>% 
      pull(PRICE) -> y2
    
    if (var(y1) > 0 & var(y2) > 0 & !is.na(var(y1)) & !is.na(var(y2))){
      BESTout.L.bannamei_BAP <- BESTmcmc(y1, y2,
                                    numSavedSteps = 10000,
                                    burnInSteps = 5000,
                                    thinSteps = 5,
                                    parallel = TRUE)
      
      
    }
  saveRDS(BESTout.L.bannamei_BAP, "RData/L_vannamei_BAP_test_results.rds")
} else {
  BESTout.L.bannamei_BAP <- readRDS("RData/L_vannamei_BAP_test_results.rds")
}

p.dif.gt.0 <- summary(BESTout.L.setiferus.FairTrade)["muDiff", "%>compVal"] * 0.01

p.dif.gt.0.df <- data.frame(p = p.dif.gt.0)
```


```{r BAP_L_vannamei_test_plot, echo=FALSE}

ggplot(L.vannamei.BAP.data) +
  geom_boxplot(aes(x = as.factor(BAP_1), 
                   y = (PRICE))) +
  #scale_color_discrete(labels = c("BAP", "Others")) + 
  #guides(color = guide_legend(title = NULL)) +
  # theme(axis.text.x = element_text(angle = 90, vjust = 0.5, 
  #                                  hjust = 1, size = 12)) +
  scale_x_discrete(labels = c("BAP", "Other")) +
  labs(x = "", title = "L. vannamei") + 
  geom_text(data = p.dif.gt.0.df,
            aes(x = 1, 
                y = max(L.vannamei.BAP.data$PRICE), 
                label = signif(p, 2)))

```


## E.	BAP giant tiger prawn (farmed)
Please compare price/lb of the same species, size and fresh/farmed with & w/o these labels

*Penaeus monodon*
```{r P_monodon_data, echo=FALSE}
main.data %>% select(DATE, ZIP, LATITUDE, LONGITUDE, MKT_NAME,
         SPP_GROUP, DSPPGRP, PRICE, COUNTRY, DCONDITION, SHRIMP,
         SPECIES, MBA, MSC, BAP) %>%
  filter(SPECIES == "Penaeus monodon") %>%
  filter(is.na(MSC))  %>% # remove MSC certified
  filter(is.na(MBA))  %>% # remove BAP certified
  mutate(BAP_1 = ifelse(is.na(BAP), 2, 1)) -> P.monodon.BAP.data

# find which levels are available as pairs:
P.monodon.BAP.data %>% 
  filter(BAP_1 == 1) %>%
  summarize(n = n()) ->P.monodon.BAP_1.summary

P.monodon.BAP.data %>% 
  filter(BAP_1 == 2) %>%
  summarize(n = n()) -> P.monodon.BAP_2.summary

```



```{r BAP_P_monodon_test, echo=FALSE, include=FALSE, cache=TRUE}

if (!file.exists("RData/P_monodon_BAP_test_results.rds")){

    P.monodon.BAP.data %>% filter(BAP_1 == 1) %>% 
      pull(PRICE) -> y1
    
    P.monodon.BAP.data %>% filter(BAP_1 == 2) %>% 
      pull(PRICE) -> y2
    
    if (var(y1) > 0 & var(y2) > 0 & !is.na(var(y1)) & !is.na(var(y2))){
      BESTout.P.monodon_BAP <- BESTmcmc(y1, y2,
                                    numSavedSteps = 10000,
                                    burnInSteps = 5000,
                                    thinSteps = 5,
                                    parallel = TRUE)
      
      
    }
  saveRDS(BESTout.P.monodon_BAP, "RData/P_monodon_BAP_test_results.rds")
} else {
  BESTout.P.monodon_BAP <- readRDS("RData/P_monodon_BAP_test_results.rds")
}

p.dif.gt.0 <- summary(BESTout.P.monodon_BAP)["muDiff", "%>compVal"] * 0.01

p.dif.gt.0.df <- data.frame(p = p.dif.gt.0)
```


```{r BAP_P_monodon_test_plot, echo=FALSE}

ggplot(P.monodon.BAP.data) +
  geom_boxplot(aes(x = as.factor(BAP_1), 
                   y = (PRICE))) +
  #scale_color_discrete(labels = c("BAP", "Others")) + 
  #guides(color = guide_legend(title = NULL)) +
  # theme(axis.text.x = element_text(angle = 90, vjust = 0.5, 
  #                                  hjust = 1, size = 12)) +
  scale_x_discrete(labels = c("BAP", "Other")) +
  labs(x = "", title = "P. monodon") + 
  geom_text(data = p.dif.gt.0.df,
            aes(x = 1, 
                y = max(P.monodon.BAP.data$PRICE), 
                label = signif(p, 2)))

```


# 3.	Litopenaeus (white or whiteleg shrimp) - price for wild-ecolabel; wild-no ecolabel; farmed- ecolabel; farmed-no ecolabel. 
*Litopenaeus setiferus* and *Litopenaeus vannamei*

Wild ecolabel vs. Wild no ecolabel vs. farmed ecolabel vs. farmed no ecolabel
```{r Litopenaeus_data, echo=FALSE}
main.data %>% select(DATE, ZIP, LATITUDE, LONGITUDE, MKT_NAME,
         SPP_GROUP, DSPPGRP, PRICE, COUNTRY, DCONDITION, SHRIMP,
         SPECIES, MBA, MSC, BAP, PROD_METHOD, ECOLABEL, WILD, FARMED) %>%
  filter(SPECIES == "Litopenaeus setiferus" | 
           SPECIES == "Litopenaeus vannamei") %>%
  mutate(PROD_METHOD_f = as.factor(PROD_METHOD),
         ECOLABEL_f = as.factor(ECOLABEL),
         ECOLABEL_I = ifelse(is.na(ECOLABEL), 0, 1),
         WILD_I = ifelse(is.na(WILD), 0, 1)) %>%
  mutate(GRP = ifelse((WILD_I == 1 & ECOLABEL_I == 1), 1,   # wild and ecolabel
                      ifelse((WILD_I == 1 & ECOLABEL_I == 0), 2,   # wild and non-ecolabel
                             ifelse((WILD_I == 0 & ECOLABEL_I == 1), 3, 4)))) -> Litopenaeus.data

# sample sizes for different groups:
Litopenaeus.data %>% 
  filter(GRP == 1) %>%
  summarize(n = n()) ->Litopenaeus_data_1.summary

Litopenaeus.data %>% 
  filter(GRP == 2) %>%
  summarize(n = n()) -> Litopenaeus_data_2.summary

Litopenaeus.data %>% 
  filter(GRP == 3) %>%
  summarize(n = n()) ->Litopenaeus_data_3.summary

Litopenaeus.data %>% 
  filter(GRP == 4) %>%
  summarize(n = n()) -> Litopenaeus_data_4.summary

# Need to put PRICE and GRP in a long format:
Litopenaeus.data %>% select(PRICE, GRP) %>%
  #mutate(GRP_f = as.factor(GRP)) %>%
  gather(GRP, PRICE) %>%
  mutate(GRP_f = as.factor(GRP)) -> Litopenaeus.long

Litopenaeus.long$GRP_f <- as.factor(Litopenaeus.long$GRP)

Litopenaeus.long$ID <- seq(from = 1, to = nrow(Litopenaeus.long))

tmp <- BANOVA.Normal(l1_formula = PRICE ~ GRP_f, 
                     data = data.frame(Litopenaeus.long),
                     id = Litopenaeus.long$ID,
                     l1_hyper = c(1, 1, 1))
  
```



```{r Litopenaeus_data_test, echo=FALSE, include=FALSE, cache=TRUE}

if (!file.exists("RData/Litopenaeus_test_results.rds")){

    Litopenaeus.data %>% filter(GRP == 1) %>% 
      pull(PRICE) -> y1
    
    Litopenaeus.data %>% filter(GRP == 2) %>% 
      pull(PRICE) -> y2
    
    Litopenaeus.data %>% filter(GRP == 3) %>% 
      pull(PRICE) -> y3
    
    Litopenaeus.data %>% filter(GRP == 4) %>% 
      pull(PRICE) -> y4
    
    
    if (var(y1) > 0 & var(y2) > 0 & !is.na(var(y1)) & !is.na(var(y2))){
      BESTout.P.monodon_BAP <- BESTmcmc(y1, y2,
                                    numSavedSteps = 10000,
                                    burnInSteps = 5000,
                                    thinSteps = 5,
                                    parallel = TRUE)
      
      
    }
  saveRDS(BESTout.P.monodon_BAP, "RData/Litopenaeus_test_results.rds")
} else {
  BESTout.P.monodon_BAP <- readRDS("RData/Litopenaeus_test_results.rds")
}

p.dif.gt.0 <- summary(BESTout.P.monodon_BAP)["muDiff", "%>compVal"] * 0.01

p.dif.gt.0.df <- data.frame(p = p.dif.gt.0)
```


```{r BAP_P_monodon_test_plot, echo=FALSE}

ggplot(P.monodon.BAP.data) +
  geom_boxplot(aes(x = as.factor(BAP_1), 
                   y = (PRICE))) +
  #scale_color_discrete(labels = c("BAP", "Others")) + 
  #guides(color = guide_legend(title = NULL)) +
  # theme(axis.text.x = element_text(angle = 90, vjust = 0.5, 
  #                                  hjust = 1, size = 12)) +
  scale_x_discrete(labels = c("BAP", "Other")) +
  labs(x = "", title = "P. monodon") + 
  geom_text(data = p.dif.gt.0.df,
            aes(x = 1, 
                y = max(P.monodon.BAP.data$PRICE), 
                label = signif(p, 2)))

```

# 4.	Shrimp by processing
All penaeid shrimp - Filter by processing “head on”, “headless”, “tail on”, “tail off”, and “cooked”
	Please compare price/lb 
