---
title: "San Diego seafood market data manipulation"
output: html_notebook
---

In this document, I try to manipulate the San Diego seafood market dataset. From the spreadsheet, I extracted the data and key into separate comma-delimited text files. I converted the price column from Accounting to Numbers - $-signs are not useful in analysis. 

First bring in the necessary libraries.
```{r}
rm(list=ls())
library(tidyverse)
```


Load the main file. Because we want to make sure all variables come in the correct format, we specify the columns first.
```{r}
col.def <- cols("YEAR" = col_integer(),
                "MONTH" = col_integer(),
                "DAY" = col_integer(),
                "DATE" = col_date(format = "%m/%d/%y"),
                "ZIP" = col_integer(),
                "LATITUDE" = col_double(),
                "LONGITUDE" = col_double(),
                "MKT_NAME" = col_character(),
                "MARKETNAME" = col_integer(),
                "MARKETTYPE" = col_integer(),
                "FULL_LABEL" = col_character(),
                "COMMON_NAME" = col_character(),
                "LENGTH_CM" = col_double(),
                "FOODGRP" = col_character(),
                "SPP_GROUP" = col_character(),
                "DSPPGRP" = col_integer(),
                "SPECIES" = col_character(),
                "FAMILY" = col_character(),
                "TL" = col_double(),
                "K_YR" = col_double(),
                "PRICE" = col_double(),
                "DCOUNTRY" = col_integer(),
                "COUNTRY" = col_character(),
                "DCONDITION" = col_integer(),
                "CONDITION" = col_character(),
                "PRODUCT_TYPE" = col_character(),
                "BRAND_NAME" = col_character(),
                "PROD_METHOD" = col_integer(),
                "KEYWORD" = col_character(),
                "ECOLABEL" = col_character(),
                "SFW_RATING" = col_integer(),
                "WILD" = col_integer(),
                "FARMED" = col_integer(),
                "FRESH" = col_integer(),
                "HVINVERT" = col_integer(),
                "SHRIMP" = col_integer(),
                "LOCAL" = col_integer(),
                "LIVE" = col_integer(),
                "SUSHI" = col_integer(),
                "RESPONSIBLE" = col_integer(),
                "MSC" = col_integer(),
                "SUSTAINABLE" = col_integer(),
                "MBA" = col_integer(),
                "MBA_CARD" = col_integer(),
                "MBA_APP" = col_integer(),
                "BAP" = col_integer(),
                "DBAPSTARS" = col_integer(),
                "BAP_LEVEL" = col_character(),
                "REGION" = col_character(),
                "GEAR" = col_character(),
                "SIZE_CLASS" = col_character(),
                "SHRIMP_PROCESSING" = col_character(),
                "DPROCCOUNTRY" = col_integer(),
                "PROCESSING_COUNTRY" = col_character(),
                "HACCP" = col_integer(),
                "SIZE_GROUP" = col_character(),
                "DOLPHIN_SAFE" = col_character(),
                "OTHER_TEXT" = col_character(),
                "GF" = col_character(),
                "O3" = col_character(),
                "NONGMO" = col_integer(),
                "SUSTAIN-" = col_integer(),
                "TRAC-" = col_integer(),
                "USA STATE" = col_character())
main.data <- read_csv(file = "data/SDSEAFOOD_Master_02042019_2.csv",
                      col_types = col.def)

```

Then, bring in the keys:
```{r}
key_country <- read.csv(file = "data/SDSEAFOOD_KEY_DCOUNTRY_02012019_1.csv")
key_condition <- read.csv(file = "data/SDSEAFOOD_KEY_DCONDITION_02012019_1.csv")
key_food.grp <- read.csv(file = "data/SDSEAFOOD_KEY_DFOODGRP_02012019_1.csv")
key_market.name <- read.csv(file = "data/SDSEAFOOD_KEY_DMARKETNAME_02012019_1.csv")
key_market.type <- read.csv(file = "data/SDSEAFOOD_KEY_DMARKETTYPE_02012019_1.csv")
key_MBA <- read.csv(file = "data/SDSEAFOOD_KEY_DMBA_X_02012019_1.csv")
key_spp.grp <- read.csv(file = "data/SDSEAFOOD_KEY_DSPPGRP_02012019_1.csv")
```

These can be joined using dplyr commands. I dropped the FULL_LABEL column. 
```{r}
main.data %>% left_join(key_spp.grp, by = "DSPPGRP") %>% 
  filter(SPP_GROUP == "SHRIMP") %>%
  select(-FULL_LABEL )-> shrimp.data

head(shrimp.data)
```


Comparison of shrimp price as a function of species, eco-label, origin, processing and condition.
```{r}
fit.1 <- lm(PRICE ~ SPECIES + SIZE_CLASS + ECOLABEL + COUNTRY + SHRIMP_PROCESSING + CONDITION, 
            data = shrimp.data)


summary(fit.1)
```




