---
title: "San Diego sea food analysis - shrimp"
output: html_notebook
---

In this file, extracted data file from SD_Seafood_data.Rmd is used to analyze shrimp data. First, load necessary libraries and the data file.

```{r}
rm(list=ls())
library(tidyverse)
shrimp.data <- readRDS(file = "RData/shrimp_data.rds")
```

The first objective of the analysis is to compare price of shrimp as a function of species, eco-label, origin, processing and condition. First, I look at these factors separately.

```{r}
#SPECIES
fit.species <- lm(PRICE ~ SPECIES -1, 
            data = shrimp.data)


summary(fit.species)
```

Accoding to this analysis, shrimp price is affected by the species. We can take a look at this through a figure. 

```{r}
# define standard error function. 
SE <- function(x, na.rm=FALSE) {
  if (na.rm) x <- na.omit(x)
  sqrt(var(x)/length(x))
}

shrimp.data %>% group_by(SPECIES) %>%
  summarise(mean = mean(PRICE),
            SE = SE(PRICE),
            n = n()) -> shrimp.species
ggplot(data = shrimp.species) +
  geom_bar(aes(x = SPECIES, y = mean),
           stat = "identity") + 
  geom_errorbar(aes(x = SPECIES,
                    ymin = mean - SE, 
                    ymax = mean + SE),
                width = 0.2) + 
  geom_text(aes(x = SPECIES, y = 1,
                label = n),
            color = "white") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5),
        axis.title.x = element_blank()) + 
  labs(y = "Mean +/- SE ($)")
  
```

```{r}
#ECOLABEL
fit.ecolabel <- lm(PRICE ~ ECOLABEL -1, 
                   data = shrimp.data)


summary(fit.ecolabel)
```

Accoding to this analysis, shrimp price is affected by ecolabels. We can take a look at this through a figure. 

```{r}

shrimp.data %>% group_by(ECOLABEL) %>%
  summarise(mean = mean(PRICE),
            SE = SE(PRICE),
            n = n()) -> shrimp.ecolabel
ggplot(data = shrimp.ecolabel) +
  geom_bar(aes(x = ECOLABEL, y = mean),
           stat = "identity") + 
  geom_errorbar(aes(x = ECOLABEL,
                    ymin = mean - SE, 
                    ymax = mean + SE),
                width = 0.2) + 
  geom_text(aes(x = ECOLABEL, y = 1,
                label = n),
            color = "white") +   
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5),
        axis.title.x = element_blank()) + 
  labs(y = "Mean +/- SE ($)")
  
```

ORIGIN:
```{r}
#ORIGIN
fit.origin <- lm(PRICE ~ COUNTRY -1, 
                   data = shrimp.data)


summary(fit.origin)
```

Accoding to this analysis, shrimp price is affected by countries We can take a look at this through a figure. 

```{r}

shrimp.data %>% group_by(COUNTRY) %>%
  summarise(mean = mean(PRICE),
            SE = SE(PRICE),
            n = n()) -> shrimp.country
ggplot(data = shrimp.country) +
  geom_bar(aes(x = COUNTRY, y = mean),
           stat = "identity") + 
  geom_errorbar(aes(x = COUNTRY,
                    ymin = mean - SE, 
                    ymax = mean + SE),
                width = 0.2) + 
  geom_text(aes(x = COUNTRY, y = 1,
                label = n),
            color = "white") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5),
        axis.title.x = element_blank()) + 
  labs(y = "Mean +/- SE ($)")
  
```

PROCESSING:
```{r}
#PROCESSING
fit.processing <- lm(PRICE ~ SHRIMP_PROCESSING -1, 
                   data = shrimp.data)


summary(fit.processing)
```

Accoding to this analysis, shrimp price is affected by processing. We can take a look at this through a figure. 

```{r}

shrimp.data %>% group_by(SHRIMP_PROCESSING) %>%
  summarise(mean = mean(PRICE),
            SE = SE(PRICE),
            n = n()) -> shrimp.processing
ggplot(data = shrimp.processing) +
  geom_bar(aes(x = SHRIMP_PROCESSING, y = mean),
           stat = "identity") + 
  geom_errorbar(aes(x = SHRIMP_PROCESSING,
                    ymin = mean - SE, 
                    ymax = mean + SE),
                width = 0.2) + 
  geom_text(aes(x = SHRIMP_PROCESSING, y = 1,
                label = n),
            color = "white") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5),
        axis.title.x = element_blank()) + 
  labs(y = "Mean +/- SE ($)")
  
```


CONDITION:
```{r}
#CONDITION
fit.condition <- lm(PRICE ~ CONDITION -1, 
                   data = shrimp.data)


summary(fit.condition)
```

Accoding to this analysis, shrimp price is affected by processing. We can take a look at this through a figure. 

```{r}

shrimp.data %>% group_by(CONDITION) %>%
  summarise(mean = mean(PRICE),
            SE = SE(PRICE),
            n = n()) -> shrimp.condition
ggplot(data = shrimp.condition) +
  geom_bar(aes(x = CONDITION, y = mean),
           stat = "identity",
           color = "black") + 
  geom_errorbar(aes(x = CONDITION,
                    ymin = mean - SE, 
                    ymax = mean + SE),
                width = 0.2) + 
  geom_text(aes(x = CONDITION, y = 1,
                label = n),
            color = "white") + 
  theme(axis.text.x = element_text(angle = 90, 
                                   hjust = 1, 
                                   vjust = 0.5),
        axis.title.x = element_blank()) + 
  labs(y = "Mean +/- SE ($)", title = "Condition")
  
```


All of these factors affect the shrimp price in San Diego markets. Are there some interacting factors? 

```{r}
shrimp.data %>% group_by(SPECIES, ECOLABEL) %>%
  summarise(mean = mean(PRICE),
            SE = SE(PRICE),
            n = n()) %>%
  mutate(ECOLABEL2 = ifelse(is.na(ECOLABEL), "NONE", ECOLABEL),
         SPECIES2 = ifelse(is.na(SPECIES), "NONE", SPECIES)) -> shrimp.sp.eco

ggplot(data = shrimp.sp.eco) + 
  geom_point(aes(x = SPECIES2, 
                y = mean, 
                color = ECOLABEL2),
             size = 3) + 
  geom_errorbar(aes(x = SPECIES2, 
                    ymin = mean - SE, 
                    ymax = mean + SE,
                    color = ECOLABEL2),
                width = 0.2)+ 
  # geom_text(aes(x = SPECIES, 
  #               y = 1,
  #               label = n)) + 
  theme(axis.text.x = element_text(angle = 90, 
                                   hjust = 1, 
                                   vjust = 0.5),
        axis.title.x = element_blank()) + 
  labs(y = "Mean +/- SE ($)", title = "Species vs. Ecolabel")
```


```{r}
ggplot(data = shrimp.sp.eco) + 
  geom_point(aes(x = ECOLABEL2, 
                y = mean, 
                color = SPECIES2),
             size = 3) + 
  geom_errorbar(aes(x = ECOLABEL2, 
                    ymin = mean - SE, 
                    ymax = mean + SE,
                    color = SPECIES2),
                width = 0.2)+ 
  # geom_text(aes(x = SPECIES, 
  #               y = 1,
  #               label = n)) + 
  theme(axis.text.x = element_text(angle = 90, 
                                   hjust = 1, 
                                   vjust = 0.5),
        axis.title.x = element_blank()) + 
  labs(y = "Mean +/- SE ($)", title = "Species vs. Ecolabel")
```



```{r}
shrimp.data %>% group_by(SPECIES, COUNTRY) %>%
  summarise(mean = mean(PRICE),
            SE = SE(PRICE),
            n = n()) %>%
  mutate(COUNTRY2 = ifelse(is.na(COUNTRY), 
                           "NONE", COUNTRY),
         SPECIES2 = ifelse(is.na(SPECIES), "NONE", SPECIES)) -> shrimp.sp.country

ggplot(data = shrimp.sp.country) + 
  geom_point(aes(x = COUNTRY2, 
                y = mean, 
                color = SPECIES2),
             size = 3) + 
  geom_errorbar(aes(x = COUNTRY2, 
                    ymin = mean - SE, 
                    ymax = mean + SE,
                    color = SPECIES2),
                width = 0.2)+ 
  # geom_text(aes(x = SPECIES, 
  #               y = 1,
  #               label = n)) + 
  theme(axis.text.x = element_text(angle = 90, 
                                   hjust = 1, 
                                   vjust = 0.5),
        axis.title.x = element_blank()) + 
  labs(y = "Mean +/- SE ($)", title = "Country vs. Species")
```

```{r}
ggplot(data = shrimp.sp.country) + 
  geom_point(aes(x = SPECIES2, 
                y = mean, 
                color = COUNTRY2),
             size = 3) + 
  geom_errorbar(aes(x = SPECIES2, 
                    ymin = mean - SE, 
                    ymax = mean + SE,
                    color = COUNTRY2),
                width = 0.2)+ 
  # geom_text(aes(x = SPECIES, 
  #               y = 1,
  #               label = n)) + 
  theme(axis.text.x = element_text(angle = 90, 
                                   hjust = 1, 
                                   vjust = 0.5),
        axis.title.x = element_blank()) + 
  labs(y = "Mean +/- SE ($)", title = "Country vs. Species")
```


```{r}
shrimp.data %>% group_by(ECOLABEL, COUNTRY) %>%
  summarise(mean = mean(PRICE),
            SE = SE(PRICE),
            n = n()) %>%
  mutate(COUNTRY2 = ifelse(is.na(COUNTRY), 
                           "NONE", COUNTRY),
         ECOLABEL2 = ifelse(is.na(ECOLABEL),
                            "NONE", ECOLABEL)) -> shrimp.eco.country

ggplot(data = shrimp.eco.country) + 
  geom_point(aes(x = COUNTRY2, 
                y = mean, 
                color = ECOLABEL2),
             size = 3) + 
  geom_errorbar(aes(x = COUNTRY2, 
                    ymin = mean - SE, 
                    ymax = mean + SE,
                    color = ECOLABEL2),
                width = 0.2)+ 
  # geom_text(aes(x = SPECIES, 
  #               y = 1,
  #               label = n)) + 
  theme(axis.text.x = element_text(angle = 90, 
                                   hjust = 1, 
                                   vjust = 0.5),
        axis.title.x = element_blank()) + 
  labs(y = "Mean +/- SE ($)", title = "Country vs. Ecolabel")
```

```{r}
ggplot(data = shrimp.eco.country) + 
  geom_point(aes(x = ECOLABEL2, 
                y = mean, 
                color = COUNTRY2),
             size = 3) + 
  geom_errorbar(aes(x = ECOLABEL2, 
                    ymin = mean - SE, 
                    ymax = mean + SE,
                    color = COUNTRY2),
                width = 0.2)+ 
  # geom_text(aes(x = SPECIES, 
  #               y = 1,
  #               label = n)) + 
  theme(axis.text.x = element_text(angle = 90, 
                                   hjust = 1, 
                                   vjust = 0.5),
        axis.title.x = element_blank()) + 
  labs(y = "Mean +/- SE ($)", title = "Country vs. Ecolabel")
```


```{r}
shrimp.data %>% group_by(SPECIES, CONDITION) %>%
  summarise(mean = mean(PRICE),
            SE = SE(PRICE),
            n = n()) %>%
  mutate(SPECIES2 = ifelse(is.na(SPECIES), 
                           "NONE", SPECIES),
         CONDITION2 = ifelse(is.na(CONDITION),
                            "NONE", CONDITION)) -> shrimp.sp.condition

ggplot(data = shrimp.sp.condition) + 
  geom_point(aes(x = SPECIES2, 
                y = mean, 
                color = CONDITION2),
             size = 3) + 
  geom_errorbar(aes(x = SPECIES2, 
                    ymin = mean - SE, 
                    ymax = mean + SE,
                    color = CONDITION2),
                width = 0.2)+ 
  # geom_text(aes(x = SPECIES, 
  #               y = 1,
  #               label = n)) + 
  theme(axis.text.x = element_text(angle = 90, 
                                   hjust = 1, 
                                   vjust = 0.5),
        axis.title.x = element_blank()) + 
  labs(y = "Mean +/- SE ($)", title = "Species vs. Condition")
```

```{r}
ggplot(data = shrimp.sp.condition) + 
  geom_point(aes(x = CONDITION2, 
                y = mean, 
                color = SPECIES2),
             size = 3) + 
  geom_errorbar(aes(x = CONDITION2, 
                    ymin = mean - SE, 
                    ymax = mean + SE,
                    color = SPECIES2),
                width = 0.2)+ 
  # geom_text(aes(x = SPECIES, 
  #               y = 1,
  #               label = n)) + 
  theme(axis.text.x = element_text(angle = 90, 
                                   hjust = 1, 
                                   vjust = 0.5),
        axis.title.x = element_blank()) + 
  labs(y = "Mean +/- SE ($)", title = "Species vs. Condition")
```


```{r}
shrimp.data %>% group_by(ECOLABEL, CONDITION) %>%
  summarise(mean = mean(PRICE),
            SE = SE(PRICE),
            n = n()) %>%
  mutate(ECOLABEL2 = ifelse(is.na(ECOLABEL), 
                           "NONE", ECOLABEL),
         CONDITION2 = ifelse(is.na(CONDITION),
                            "NONE", CONDITION)) -> shrimp.eco.condition

ggplot(data = shrimp.eco.condition) + 
  geom_point(aes(x = CONDITION2, 
                y = mean, 
                color = ECOLABEL2),
             size = 3) + 
  geom_errorbar(aes(x = CONDITION2, 
                    ymin = mean - SE, 
                    ymax = mean + SE,
                    color = ECOLABEL2),
                width = 0.2)+ 
  # geom_text(aes(x = SPECIES, 
  #               y = 1,
  #               label = n)) + 
  theme(axis.text.x = element_text(angle = 90, 
                                   hjust = 1, 
                                   vjust = 0.5),
        axis.title.x = element_blank()) + 
  labs(y = "Mean +/- SE ($)", title = "Ecolabel vs. Condition")
```


```{r}
ggplot(data = shrimp.eco.condition) + 
  geom_point(aes(x = ECOLABEL2, 
                y = mean, 
                color = CONDITION2),
             size = 3) + 
  geom_errorbar(aes(x = ECOLABEL2, 
                    ymin = mean - SE, 
                    ymax = mean + SE,
                    color = CONDITION2),
                width = 0.2)+ 
  # geom_text(aes(x = SPECIES, 
  #               y = 1,
  #               label = n)) + 
  theme(axis.text.x = element_text(angle = 90, 
                                   hjust = 1, 
                                   vjust = 0.5),
        axis.title.x = element_blank()) + 
  labs(y = "Mean +/- SE ($)", title = "Ecolabel vs. Condition")
```


```{r}
shrimp.data %>% group_by(COUNTRY, CONDITION) %>%
  summarise(mean = mean(PRICE),
            SE = SE(PRICE),
            n = n()) %>%
  mutate(COUNTRY2 = ifelse(is.na(COUNTRY), 
                           "NONE", COUNTRY),
         CONDITION2 = ifelse(is.na(CONDITION),
                            "NONE", CONDITION)) -> shrimp.country.condition

ggplot(data = shrimp.country.condition) + 
  geom_point(aes(x = COUNTRY2, 
                y = mean, 
                color = CONDITION2),
             size = 3) + 
  geom_errorbar(aes(x = COUNTRY2, 
                    ymin = mean - SE, 
                    ymax = mean + SE,
                    color = CONDITION2),
                width = 0.2)+ 
  # geom_text(aes(x = SPECIES, 
  #               y = 1,
  #               label = n)) + 
  theme(axis.text.x = element_text(angle = 90, 
                                   hjust = 1, 
                                   vjust = 0.5),
        axis.title.x = element_blank()) + 
  labs(y = "Mean +/- SE ($)", title = "Country vs. Condition")
```

```{r}
ggplot(data = shrimp.country.condition) + 
  geom_point(aes(x = CONDITION2, 
                y = mean, 
                color = COUNTRY2),
             size = 3) + 
  geom_errorbar(aes(x = CONDITION2, 
                    ymin = mean - SE, 
                    ymax = mean + SE,
                    color = COUNTRY2),
                width = 0.2)+ 
  # geom_text(aes(x = SPECIES, 
  #               y = 1,
  #               label = n)) + 
  theme(axis.text.x = element_text(angle = 90, 
                                   hjust = 1, 
                                   vjust = 0.5),
        axis.title.x = element_blank()) + 
  labs(y = "Mean +/- SE ($)", title = "Country vs. Condition")
```


```{r}
shrimp.data %>% group_by(SHRIMP_PROCESSING, CONDITION) %>%
  summarise(mean = mean(PRICE),
            SE = SE(PRICE),
            n = n()) %>%
  mutate(PROCESSING2 = ifelse(is.na(SHRIMP_PROCESSING), 
                           "NONE", SHRIMP_PROCESSING),
         CONDITION2 = ifelse(is.na(CONDITION),
                            "NONE", CONDITION)) -> shrimp.proc.condition

ggplot(data = shrimp.proc.condition) + 
  geom_point(aes(x = PROCESSING2, 
                y = mean, 
                color = CONDITION2),
             size = 3) + 
  geom_errorbar(aes(x = PROCESSING2, 
                    ymin = mean - SE, 
                    ymax = mean + SE,
                    color = CONDITION2),
                width = 0.2)+ 
  # geom_text(aes(x = SPECIES, 
  #               y = 1,
  #               label = n)) + 
  theme(axis.text.x = element_text(angle = 90, 
                                   hjust = 1, 
                                   vjust = 0.5),
        axis.title.x = element_blank()) + 
  labs(y = "Mean +/- SE ($)", title = "Processing vs. Condition")
```

```{r}
ggplot(data = shrimp.proc.condition) + 
  geom_point(aes(x = CONDITION2, 
                y = mean, 
                color = PROCESSING2),
             size = 3) + 
  geom_errorbar(aes(x = CONDITION2, 
                    ymin = mean - SE, 
                    ymax = mean + SE,
                    color = PROCESSING2),
                width = 0.2)+ 
  # geom_text(aes(x = SPECIES, 
  #               y = 1,
  #               label = n)) + 
  theme(axis.text.x = element_text(angle = 90, 
                                   hjust = 1, 
                                   vjust = 0.5),
        axis.title.x = element_blank()) + 
  labs(y = "Mean +/- SE ($)", title = "Processing vs. Condition")
```


```{r}
shrimp.data %>% group_by(SHRIMP_PROCESSING, ECOLABEL) %>%
  summarise(mean = mean(PRICE),
            SE = SE(PRICE),
            n = n()) %>%
  mutate(PROCESSING2 = ifelse(is.na(SHRIMP_PROCESSING), 
                           "NONE", SHRIMP_PROCESSING),
         ECOLABEL2 = ifelse(is.na(ECOLABEL),
                            "NONE", ECOLABEL)) -> shrimp.proc.eco

ggplot(data = shrimp.proc.eco) + 
  geom_point(aes(x = PROCESSING2, 
                y = mean, 
                color = ECOLABEL2),
             size = 3) + 
  geom_errorbar(aes(x = PROCESSING2, 
                    ymin = mean - SE, 
                    ymax = mean + SE,
                    color = ECOLABEL2),
                width = 0.2)+ 
  # geom_text(aes(x = SPECIES, 
  #               y = 1,
  #               label = n)) + 
  theme(axis.text.x = element_text(angle = 90, 
                                   hjust = 1, 
                                   vjust = 0.5),
        axis.title.x = element_blank()) + 
  labs(y = "Mean +/- SE ($)", title = "Processing vs. Ecolabel")
```

```{r}
ggplot(data = shrimp.proc.eco) + 
  geom_point(aes(x = ECOLABEL2, 
                y = mean, 
                color = PROCESSING2),
             size = 3) + 
  geom_errorbar(aes(x = ECOLABEL2, 
                    ymin = mean - SE, 
                    ymax = mean + SE,
                    color = PROCESSING2),
                width = 0.2)+ 
  # geom_text(aes(x = SPECIES, 
  #               y = 1,
  #               label = n)) + 
  theme(axis.text.x = element_text(angle = 90, 
                                   hjust = 1, 
                                   vjust = 0.5),
        axis.title.x = element_blank()) + 
  labs(y = "Mean +/- SE ($)", title = "Processing vs. Ecolabel")
```


```{r}
shrimp.data %>% group_by(SHRIMP_PROCESSING, SPECIES) %>%
  summarise(mean = mean(PRICE),
            SE = SE(PRICE),
            n = n()) %>%
  mutate(PROCESSING2 = ifelse(is.na(SHRIMP_PROCESSING), 
                           "NONE", SHRIMP_PROCESSING),
         SPECIES2 = ifelse(is.na(SPECIES),
                            "NONE", SPECIES)) -> shrimp.proc.sp

ggplot(data = shrimp.proc.sp) + 
  geom_point(aes(x = PROCESSING2, 
                y = mean, 
                color = SPECIES2),
             size = 3) + 
  geom_errorbar(aes(x = PROCESSING2, 
                    ymin = mean - SE, 
                    ymax = mean + SE,
                    color = SPECIES2),
                width = 0.2)+ 
  # geom_text(aes(x = SPECIES, 
  #               y = 1,
  #               label = n)) + 
  theme(axis.text.x = element_text(angle = 90, 
                                   hjust = 1, 
                                   vjust = 0.5),
        axis.title.x = element_blank()) + 
  labs(y = "Mean +/- SE ($)", title = "Processing vs. Species")
```


```{r}
ggplot(data = shrimp.proc.sp) + 
  geom_point(aes(x = SPECIES2, 
                y = mean, 
                color = PROCESSING2),
             size = 3) + 
  geom_errorbar(aes(x = SPECIES2, 
                    ymin = mean - SE, 
                    ymax = mean + SE,
                    color = PROCESSING2),
                width = 0.2)+ 
  # geom_text(aes(x = SPECIES, 
  #               y = 1,
  #               label = n)) + 
  theme(axis.text.x = element_text(angle = 90, 
                                   hjust = 1, 
                                   vjust = 0.5),
        axis.title.x = element_blank()) + 
  labs(y = "Mean +/- SE ($)", title = "Processing vs. Species")
```

```{r}
shrimp.data %>% group_by(SHRIMP_PROCESSING, COUNTRY) %>%
  summarise(mean = mean(PRICE),
            SE = SE(PRICE),
            n = n()) %>%
  mutate(PROCESSING2 = ifelse(is.na(SHRIMP_PROCESSING), 
                           "NONE", SHRIMP_PROCESSING),
         COUNTRY2 = ifelse(is.na(COUNTRY),
                            "NONE", COUNTRY)) -> shrimp.proc.country

ggplot(data = shrimp.proc.country) + 
  geom_point(aes(x = PROCESSING2, 
                y = mean, 
                color = COUNTRY2),
             size = 3) + 
  geom_errorbar(aes(x = PROCESSING2, 
                    ymin = mean - SE, 
                    ymax = mean + SE,
                    color = COUNTRY2),
                width = 0.2)+ 
  # geom_text(aes(x = SPECIES, 
  #               y = 1,
  #               label = n)) + 
  theme(axis.text.x = element_text(angle = 90, 
                                   hjust = 1, 
                                   vjust = 0.5),
        axis.title.x = element_blank()) + 
  labs(y = "Mean +/- SE ($)", title = "Processing vs. Country")
```


```{r}
ggplot(data = shrimp.proc.country) + 
  geom_point(aes(x = COUNTRY2, 
                y = mean, 
                color = PROCESSING2),
             size = 3) + 
  geom_errorbar(aes(x = COUNTRY2, 
                    ymin = mean - SE, 
                    ymax = mean + SE,
                    color = PROCESSING2),
                width = 0.2)+ 
  # geom_text(aes(x = SPECIES, 
  #               y = 1,
  #               label = n)) + 
  theme(axis.text.x = element_text(angle = 90, 
                                   hjust = 1, 
                                   vjust = 0.5),
        axis.title.x = element_blank()) + 
  labs(y = "Mean +/- SE ($)", title = "Processing vs. Country")
```
