---
title: "Variable selection for shrimp data with conditional random forest"
output: html_notebook
---

This notebook describes the variable selection process for predicting the price of shrimp from various predictors using conditional random forest (cRF). This approach of regression tree and bagging procedure is different from the original random forest in the way it selects variables.  Variable selection statistics for each variable is calculated conditional on other variables. This apparently is more robust to correlated variables.  

The conditional random forest approach is used to select variables that are most useful in predicting the price of shrimp. Then the relationships between each of the selected variables and price are examined. 

In the next section, I converted categorical variables into integer variables.  This was unnecessary but easier to deal with than having named categories.  
```{r}
rm(list=ls())
library(tidyverse)
library(party)
library(rfPermute)
library(randomForestExplainer)

ntree <- 5000

shrimp.data.raw <- readRDS(file = "RData/shrimp_data.rds")

source("shrimp_analysis_fcns.R")
shrimp.data <- shrimp.data.fcn(shrimp.data.raw)

# add wild vs. aquaculture
# then look just one at a time.

# production method = 1 (wild) 2 (farmed)

# check to see if converted right
shrimp.data %>% select(SPECIES, SP_GROUP, 
                       SIZE_GROUP2, SIZE_GROUP, SIZE_GROUP_NUM,
                       SHRIMP_PROCESSING, SHRIMP_PROCESSING_NUM,
                       ECOLABEL, ECOLABEL2, PROD_METHOD) %>%
  #filter(SHRIMP_PROCESSING == "CKD TON") -> tmp
  filter(SIZE_GROUP == "Extra Large")->tmp
  #filter(is.na(SIZE_GROUP))-> tmp
```

We may include more variables in the next attempt but I thought this may be a good place to start.  Here I further change the variables into factor variables as the numbers don't mean much for these variables. I also added a variable of random numbers (RV) as a yardstick to which all variables are compared. If a variable is less useful than random numbers for predicing the price, they are not very useful. 

```{r}
shrimp.data.RF <- RF.shrimp.data(shrimp.data)

M.1 <- as.formula("PRICE ~ SP_GROUP_f+
                       SIZE_GROUP_f +
                       SHRIMP_PROCESSING_f +
                       YEAR + ZIP_f + MARKETTYPE_f +
                       ECOLABEL_f + PROD_METHOD_f + RV")

#p <- length(attr(terms(M.1), "term.labels"))
# floor(sqrt(p)) and try half and 2x that
#mtry <- floor(sqrt(p)/2)
#mtry <- floor(sqrt(p))
  
if (!file.exists("RData/cRF_M_1_out.rds")){
  cRF.M.1 <- cforest(formula = M.1,
                    data = shrimp.data.RF,
                    control = cforest_unbiased(ntree = ntree,
                                               trace = 500))
  
  saveRDS(cRF.M.1, file = "RData/cRF_M_1_out.rds")
  
} else {
  cRF.M.1 <- readRDS("RData/cRF_M_1_out.rds")
}

```

Predict the price using the model and find the variable importance:
```{r}
predict.all <- predict.cRF(cRF.M.1,
                           outfilename = "RData/cRF_M_1_predict.rds")

fit.all <- fit.cRF(predicted = predict.all,
                   df = shrimp.data.RF)

var.imp.cRF.df <- var.imp.shrimp(cRF.out = cRF.M.1,
                              outfile = "RData/cRF_M_1_varImp.rds")

print(fit.all$R2)


```

The vairance explained is pseudo.R2 = 0.77 as of Feb 25, 2019, using "PRICE ~ SP_GROUP_f+SIZE_GROUP_f + SHRIMP_PROCESSING_f + YEAR + ZIP_f + MARKETTYPE_f + ECOLABEL_f + PROD_METHOD_f + RV". Now, it is 0.71... how the hell did I get 0.77 before? 

Look at the variable importance:
```{r}
var.imp.cRF.df %>% mutate(var_name = case_when(Variable == "SIZE_GROUP_f" ~ "SIZE",
                                                Variable == "ZIP_f" ~ "ZIP",
                                                Variable == "PROD_METHOD_f" ~ "WILD/FARM",
                                                Variable == "MARKETTYPE_f" ~ "MARKET",
                                                Variable == "SHRIMP_PROCESSING_f" ~ "PROCESSING",
                                                Variable == "SP_GROUP_f" ~ "SPECIES",
                                                Variable == "ECOLABEL_f" ~ "ECOLABEL",
                                                Variable == "YEAR" ~ "YEAR",
                                                Variable == "RV" ~ "RANDOM",
                                                TRUE ~ NA_character_)) -> var.imp.cRF.df

p.1 <- ggplot(data = var.imp.cRF.df) + 
  geom_point(aes(x = var.imp, 
                 y = reorder(var_name, var.imp)),
             size = 3) + 
  theme_bw() + 
  labs(x = "Variable importance") + 
  theme(axis.title.y = element_blank(),
        axis.title.x = element_text(size =12))

ggsave(p.1, 
       filename = "figures/varImp_cRF.png", 
       device = "png", dpi = 600)
print(p.1)
```

The variable importance metric is the mean difference in MSEs between out-of-bag (OOB) predictions and those from one variable permuted. The mean is computed from all trees and the mean divided by the standard deviation of the differences. 

This plot indicates that size groups affect the prediction of price the most. Zipcode affects more than ecolabels. Interesting!  

Next, I look at the relationship between predicted and observed. If the prediction is perfect, the plot should be on the y = x line. 

```{r}
p.2 <- ggplot(data = fit.all$df) + 
  geom_point(aes(x = PRICE, y = PREDICT)) + 
  geom_abline(slope = 1, intercept = 0,
              size = 1.2) + 
  labs(x = "Observed price ($/lb)", y = "Predicted price ($/lb)")

ggsave(p.2, 
       filename = "figures/ObsVsPred_cRF.png", 
       device = "png", dpi = 600)
print(p.2)

```



```{r}
# find the sample size for each category:
fit.all$df %>% group_by(SIZE_GROUP_f) %>%
  summarize(n = n()) -> size.n

p.3 <- ggplot() + 
  geom_boxplot(data = fit.all$df,
               aes(x = SIZE_GROUP_f, y = PREDICT)) +
  scale_x_discrete(breaks = c("1", "2", "3", "4", "5", "6", "7", "8", "9"),
                   labels = c("Tiny", "Small", "Medium", "Large", 
                              "Extra Large", "Jumbo", "Extra Jumbo", 
                              "Colossal", "Extra Colossal")) + 
  geom_text(data = size.n,
            aes(x = SIZE_GROUP_f, y = 1, label = n), 
            size = 3) + 
  labs(x = "", y = "Predicted price ($/lb)") +
  theme(axis.text.x = element_text(angle = 90, 
                                   vjust = 0.5, 
                                   hjust = 1, size = 12))

ggsave(p.3, 
       filename = "figures/sizeVsPred_cRF.png", 
       device = "png", dpi = 600)
print(p.3)
```

```{r}
fit.all$df %>% group_by(ZIP_f) %>%
  summarise(mean_by_ZIP = mean(PREDICT), n = n())-> mean.PRICE.by.ZIP

p.4 <- ggplot(data = mean.PRICE.by.ZIP) + 
  geom_point(aes(x = reorder(ZIP_f, mean_by_ZIP),
                 y = mean_by_ZIP),
             size = 3) +
  geom_text(aes(x = ZIP_f, y = 3, label = n), 
            size = 3, angle = 90, hjust = 1, vjust = 0.5) + 
  labs(x = "", y = "Predicted mean price ($/lb)") +
  theme(axis.text.x = element_text(angle = 90, 
                                   vjust = 0.5, 
                                   hjust = 0.5,
                                   size = 10)) + 
  ylim(c(2, 22))
  
ggsave(p.4, 
       filename = "figures/zipVsPred_cRF.png", 
       device = "png", dpi = 600)
print(p.4)

```

```{r}
zip.order <- reorder(mean.PRICE.by.ZIP$ZIP_f, 
                     mean.PRICE.by.ZIP$mean_by_ZIP)

fit.all$df$ZIP_ordered <- factor(fit.all$df$ZIP_f,
                                     ordered = TRUE,
                                     levels = levels(zip.order))
p.5 <- ggplot(data = fit.all$df) + 
  geom_boxplot(aes(x = ZIP_ordered, 
                   y = PREDICT)) + 
  labs(x = "", y = "Predicted price ($/lb)") +
  theme(axis.text.x = element_text(angle = 90, 
                                   vjust = 0.5, 
                                   hjust = 1)) 

print(p.5)
```

```{r}
p.6 <- ggplot(data = fit.all$df) + 
  geom_boxplot(aes(x = ZIP_ordered, 
                   y = PRICE)) + 
  labs(x = "", y = "Observed price ($/lb)") +
  theme(axis.text.x = element_text(angle = 90, 
                                   vjust = 0.5, 
                                   hjust = 1)) 
ggsave(p.6, 
       filename = "figures/zipVsObs_cRF.png", 
       device = "png", dpi = 600)
print(p.6)
```


```{r}
p.7 <- ggplot(data = fit.all$df) + 
  geom_boxplot(aes(x = PROD_METHOD_f, y = PREDICT))+
  scale_x_discrete(breaks = c("1", "2"),
                   labels = c("Wild", "Farmed")) + 
  labs(x = "", y = "Predicted price ($/lb)") +
  theme(axis.text = element_text(size = 12),
        axis.title.y = element_text(size = 12))
print(p.7)
```

```{r}
shrimp.data.RF %>% filter(PROD_METHOD_f == "1") -> shrimp.data.wild.RF

M.1.wild <- as.formula("PRICE ~ SP_GROUP_f+
                       SIZE_GROUP_f +
                       SHRIMP_PROCESSING_f +
                       YEAR + ZIP_f + MARKETTYPE_f +
                       ECOLABEL_f + RV")

#p <- length(attr(terms(M.1), "term.labels"))
# floor(sqrt(p)) and try half and 2x that
#mtry <- floor(sqrt(p)/2)
#mtry <- floor(sqrt(p))
  
if (!file.exists("RData/cRF_M_1_wild_out.rds")){
  cRF.M.1.wild <- cforest(formula = M.1.wild,
                    data = shrimp.data.wild.RF,
                    control = cforest_unbiased(ntree = ntree,
                                               trace = 500))
  
  saveRDS(cRF.M.1.wild, file = "RData/cRF_M_1_wild_out.rds")
  
} else {
  cRF.M.1.wild <- readRDS("RData/cRF_M_1_wild_out.rds")
}

```

Predict the price using the model and find the variable importance:
```{r}
predict.wild <- predict.cRF(cRF.M.1.wild,
                            outfilename = "RData/cRF_M_1_wild_predict.rds")

fit.wild <- fit.cRF(predicted = predict.wild,
                    df = shrimp.data.wild.RF)

var.imp.wild.cRF <- var.imp.shrimp(cRF.out = cRF.M.1.wild,
                                   outfile = "RData/cRF_M_1_wild_varImp.rds")

var.imp.wild.cRF %>% mutate(var_name = case_when(Variable == "SIZE_GROUP_f" ~ "SIZE",
                                                Variable == "ZIP_f" ~ "ZIP",
                                                Variable == "MARKETTYPE_f" ~ "MARKET",
                                                Variable == "SHRIMP_PROCESSING_f" ~ "PROCESSING",
                                                Variable == "SP_GROUP_f" ~ "SPECIES",
                                                Variable == "ECOLABEL_f" ~ "ECOLABEL",
                                                Variable == "YEAR" ~ "YEAR",
                                                Variable == "RV" ~ "RANDOM",
                                                TRUE ~ NA_character_)) -> var.imp.wild.cRF

print(fit.wild$R2)
```

```{r}
p.8 <- ggplot(data = var.imp.wild.cRF) + 
  geom_point(aes(x = var.imp, 
                 y = reorder(var_name, var.imp)),
             size = 3) + 
  theme_bw() + 
  labs(x = "Variable importance") + 
  theme(axis.title.y = element_blank(),
        axis.title.x = element_text(size =12))

ggsave(p.8, 
       filename = "figures/varImp_Wild_cRF.png", 
       device = "png", dpi = 600)
print(p.8)

```

```{r}
p.9 <- ggplot(data = fit.wild$df) + 
  geom_point(aes(x = PRICE, y = PREDICT)) + 
  geom_abline(slope = 1, intercept = 0,
              size = 1.2) + 
  labs(x = "Observed price ($/lb)", y = "Predicted price ($/lb)")

ggsave(p.9, 
       filename = "figures/ObsVsPred_Wild_cRF.png", 
       device = "png", dpi = 600)
print(p.9)

```



```{r}
fit.wild$df %>% group_by(SIZE_GROUP_f) %>%
  summarize(n = n()) -> wild.size.n

p.10 <- ggplot(data = fit.wild$df) + 
  geom_boxplot(aes(x = SIZE_GROUP_f, y = PREDICT)) +
  scale_x_discrete(breaks = c("1", "2", "3", "4", "5", "6", "7", "8", "9"),
                   labels = c("Tiny", "Small", "Medium", "Large", 
                              "Extra Large", "Jumbo", "Extra Jumbo", 
                              "Colossal", "Extra Colossal")) + 
  geom_text(data = wild.size.n,
            aes(x = SIZE_GROUP_f, y = 3, label = n), 
            size = 3) + 
  labs(x = "", y = "Predicted price ($/lb)") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, 
                                   hjust = 1, size = 12))

ggsave(p.10, 
       filename = "figures/sizeVsPred_wild_cRF.png", 
       device = "png", dpi = 600)
print(p.10)
```

```{r}
shrimp.data.RF %>% filter(PROD_METHOD_f == "2") -> shrimp.data.farm.RF

if (!file.exists("RData/cRF_M_1_farm_out.rds")){
  cRF.M.1.farm <- cforest(formula = M.1.wild,
                    data = shrimp.data.farm.RF,
                    control = cforest_unbiased(ntree = ntree,
                                               trace = 500))
  
  saveRDS(cRF.M.1.farm, file = "RData/cRF_M_1_farm_out.rds")
  
} else {
  cRF.M.1.farm <- readRDS("RData/cRF_M_1_farm_out.rds")
}

```

Predict the price using the model and find the variable importance:
```{r}
predict.farm <- predict.cRF(cRF.M.1.farm,
                            outfilename = "RData/cRF_M_1_farm_predict.rds")

fit.farm <- fit.cRF(predicted = predict.farm,
                    df = shrimp.data.farm.RF)

var.imp.farm.cRF <- var.imp.shrimp(cRF.out = cRF.M.1.farm,
                                   outfile = "RData/cRF_M_1_farm_varImp.rds")

var.imp.farm.cRF %>% mutate(var_name = case_when(Variable == "SIZE_GROUP_f" ~ "SIZE",
                                                Variable == "ZIP_f" ~ "ZIP",
                                                Variable == "MARKETTYPE_f" ~ "MARKET",
                                                Variable == "SHRIMP_PROCESSING_f" ~ "PROCESSING",
                                                Variable == "SP_GROUP_f" ~ "SPECIES",
                                                Variable == "ECOLABEL_f" ~ "ECOLABEL",
                                                Variable == "YEAR" ~ "YEAR",
                                                Variable == "RV" ~ "RANDOM",
                                                TRUE ~ NA_character_)) -> var.imp.farm.cRF

print(fit.farm$R2)
```

```{r}
p.11 <- ggplot(data = var.imp.farm.cRF) + 
  geom_point(aes(x = var.imp, 
                 y = reorder(var_name, var.imp)),
             size = 3) + 
  theme_bw() + 
  labs(x = "Variable importance") + 
  theme(axis.title.y = element_blank(),
        axis.title.x = element_text(size =12))

ggsave(p.11, 
       filename = "figures/varImp_farm_cRF.png", 
       device = "png", dpi = 600)
print(p.11)

```

```{r}
p.12 <- ggplot(data = fit.farm$df) + 
  geom_point(aes(x = PRICE, y = PREDICT)) + 
  geom_abline(slope = 1, intercept = 0,
              size = 1.2) + 
  labs(x = "Observed price ($)", y = "Predicted price ($)")

ggsave(p.12, 
       filename = "figures/ObsVsPred_farm_cRF.png", 
       device = "png", dpi = 600)
print(p.12)

```



```{r}
fit.farm$df %>% group_by(SIZE_GROUP_f) %>%
  summarize(n = n()) -> farm.size.n

p.13 <- ggplot(data = fit.farm$df) + 
  geom_boxplot(aes(x = SIZE_GROUP_f, y = PREDICT)) +
  scale_x_discrete(breaks = c("1", "2", "3", "4", "5", "6", "7", "8", "9"),
                   labels = c("Tiny", "Small", "Medium", "Large", 
                              "Extra Large", "Jumbo", "Extra Jumbo", 
                              "Colossal", "Extra Collossal")) + 
  geom_text(data = farm.size.n,
            aes(x = SIZE_GROUP_f, y = 3, label = n), 
            size = 3) + 
  labs(x = "", y = "Predicted price ($/lb)") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, 
                                   hjust = 1, size = 12))

ggsave(p.13, 
       filename = "figures/sizeVsPred_farm_cRF.png", 
       device = "png", dpi = 600)
print(p.13)
```


```{r}
fit.farm$df %>% group_by(ZIP_f) %>%
  summarise(mean_by_ZIP = mean(PREDICT),
            n = n())-> mean.PRICE.farm.by.ZIP

p.16 <- ggplot(data = mean.PRICE.farm.by.ZIP) + 
  geom_point(aes(x = reorder(ZIP_f, mean_by_ZIP),
                 y = mean_by_ZIP),
             size = 3) +
  geom_text(aes(x = ZIP_f, y = 3, label = n), 
            size = 3, angle = 90, hjust = 1, vjust = 0.5) + 
  labs(x = "", y = "Predicted mean price ($/lb)") +
  theme(axis.text.x = element_text(angle = 90, 
                                   vjust = 0.5, 
                                   hjust = 1)) + 
  ylim(c(2, 21))
  
ggsave(p.16, 
       filename = "figures/zipVsPred_farm_cRF.png", 
       device = "png", dpi = 600)
print(p.16)

```

```{r}
zip.order.farm <- reorder(mean.PRICE.farm.by.ZIP$ZIP_f, 
                          mean.PRICE.farm.by.ZIP$mean_by_ZIP)

fit.farm$df$ZIP_ordered <- factor(fit.farm$df$ZIP_f,
                                  ordered = TRUE,
                                  levels = levels(zip.order.farm))

p.17 <- ggplot(data = fit.farm$df) + 
  geom_boxplot(aes(x = ZIP_ordered, 
                   y = PREDICT)) + 
  labs(x = "", y = "Predicted price ($/lb)") +
  theme(axis.text.x = element_text(angle = 90, 
                                   vjust = 0.5, 
                                   hjust = 1)) 

print(p.17)
```

```{r}
p.18 <- ggplot(data = fit.farm$df) + 
  geom_boxplot(aes(x = ZIP_ordered, 
                   y = PRICE)) + 
  labs(x = "", y = "Observed price ($/lb)") +
  theme(axis.text.x = element_text(angle = 90, 
                                   vjust = 0.5, 
                                   hjust = 1)) 
ggsave(p.18, 
       filename = "figures/zipVsObs_farm_cRF.png", 
       device = "png", dpi = 600)
print(p.18)
```
