---
title: "Variable selection for shrimp data with c-RF"
output: html_notebook
---

This notebook describes the variable selection process for predicting the price of shrimp from various predictors. 

Load the libraries and data and convert some categorical variables to ordinal variables, such as size group. 
```{r}
rm(list=ls())
library(tidyverse)
library(party)
library(rfPermute)

ntree <- 500

# group Tiny and Extra Small together
# Order the size group from tiny to extra colossal
# group the species 
# we ignore MBA for this analysis
shrimp.data.raw <- readRDS(file = "RData/shrimp_data.rds")
shrimp.data <- shrimp.data.fcn(shrimp.data.raw)
# add wild vs. aquaculture

# check to see if converted right
shrimp.data %>% select(SPECIES, SP_GROUP, 
                       SIZE_GROUP2, SIZE_GROUP, SIZE_GROUP_NUM,
                       SHRIMP_PROCESSING, SHRIMP_PROCESSING_NUM,
                       ECOLABEL, ECOLABEL2) %>%
  #filter(SHRIMP_PROCESSING == "CKD TON") -> tmp
  filter(SIZE_GROUP == "Extra Large")->tmp
  #filter(is.na(SIZE_GROUP))-> tmp
```

I didn't convert the ecolabel field to numerical values because they are depending on the products, such as BAP is only for aquacultured products. But... it may not make difference when we pool all these products as a group and not have wild-aquacultured separations. Hmmm... 

```{r}
shrimp.data %>% select(SP_GROUP_f,
                       SIZE_GROUP_f,
                       SHRIMP_PROCESSING_f,
                       YEAR, ZIP,  MARKETTYPE_f, PRICE,
                       ECOLABEL_f) %>% 
  mutate(RV = runif(nrow(shrimp.data), 
                    min = 0, 
                    max = 100))  %>%
  na.omit()-> shrimp.data.RF

M.1 <- as.formula("PRICE ~ SP_GROUP_f+
                       SIZE_GROUP_f +
                       SHRIMP_PROCESSING_f +
                       YEAR + ZIP + MARKETTYPE_f +
                       ECOLABEL_f + RV")

#p <- length(attr(terms(M.1), "term.labels"))
# floor(sqrt(p)) and try half and 2x that
#mtry <- floor(sqrt(p)/2)
#mtry <- floor(sqrt(p))
  
if (!file.exists("RData/RF_M_1_out.rds")){
  RF.M.1 <- cforest(formula = M.1,
                    data = shrimp.data.RF,
                    control = cforest_unbiased(ntree = ntree,
                                               trace = 500))
  saveRDS(RF.M.1, file = "RData/RF_M_1_out.rds")
  
} else {
  RF.M.1 <- readRDS("RData/RF_M_1_out.rds")
}

```

Find the variable importance:
```{r}
if (!file.exists("RData/RF_M_1_varImp.rds")){
  var.imp <- sort(varimp(RF.M.1), decreasing = FALSE)
  saveRDS(var.imp, file = "RData/RF_M_1_varImp.rds")
} else {
  var.imp <- readRDS("RData/RF_M_1_varImp.rds")
}

if (!file.exists("RData/RF_M_1_predict.rds")){
  pred.RF.M.1 <- predict(RF.M.1, newdata = NULL)
  saveRDS(pred.RF.M.1, file = "RData/RF_M_1_predict.rds")
} else {
  pred.RF.M.1 <- readRDS("RData/RF_M_1_predict.rds")
}
```

Look at the variable importance:
```{r}
var.imp.df <- data.frame(var.imp)
var.imp.df$Variable <- rownames(var.imp.df)

ggplot(data = var.imp.df) + 
  geom_point(aes(x = var.imp, y = reorder(Variable, var.imp)),
             size = 3) + 
  theme_bw() + 
  labs(x = "Variable importance") + 
  theme(axis.title.y = element_blank(),
        axis.title.x = element_text(size =12))
```

This plot indicates that size groups affect the prediction of price the most. Zipcode affects more than ecolabels. Interesting!  

Let's use another method to see how that comes out.
```{r}

if (!file.exists("RData/RFpermute_M_1.rds")){
  var.imp.rfPermute <- rfPermute(formula = M.1,
                                 data = shrimp.data.RF,
                                 ntree = ntree)
  saveRDS(var.imp.rfPermute, file = "RData/RFpermute_M_1.rds")
} else {
  var.imp.rfPermute <- readRDS(file = "RData/RFpermute_M_1.rds")
  
}


```



Compare the data and predictions:

```{r}
shrimp.data.RF$PREDICTED <- pred.RF.M.1[,1]
ggplot(data = shrimp.data.RF) +
  geom_point(aes(x = PRICE, y = PREDICTED))

```

