---
title: "Variable selection for shrimp data with conditional random forest"
output: html_notebook
---

This notebook describes the variable selection process for predicting the price of shrimp from various predictors using conditional random forest (cRF). This approach of regression tree and bagging procedure is different from the original random forest in the way it selects variables.  Variable selection statistics for each variable is calculated conditional on other variables. This apparently is more robust to correlated variables.  

The conditional random forest approach is used to select variables that are most useful in predicting the price of shrimp. Then the relationships between each of the selected variables and price are examined. 

In the next section, I converted categorical variables into integer variables.  This was unnecessary but easier to deal with than having named categories.  

Look into inTree package. 2019-02-25.

```{r}
rm(list=ls())
library(tidyverse)
library(party)
library(rfPermute)
library(randomForestExplainer)
source("shrimp_analysis_fcns.R")

ntree <- 5000
shrimp.data.raw <- readRDS(file = "RData/shrimp_data.rds")
shrimp.data <- shrimp.data.fcn(shrimp.data.raw)
# add wild vs. aquaculture
# then look just one at a time.

# production method = 1 (wild) 2 (farmed)

# check to see if converted right
shrimp.data %>% select(SPECIES, SP_GROUP, 
                       SIZE_GROUP2, SIZE_GROUP, SIZE_GROUP_NUM,
                       SHRIMP_PROCESSING, SHRIMP_PROCESSING_NUM,
                       ECOLABEL, ECOLABEL2) %>%
  #filter(SHRIMP_PROCESSING == "CKD TON") -> tmp
  filter(SIZE_GROUP == "Extra Large")->tmp
  #filter(is.na(SIZE_GROUP))-> tmp
```

We may include more variables in the next attempt but I thought this may be a good place to start.  Here I further change the variables into factor variables as the numbers don't mean much for these variables. I also added a variable of random numbers (RV) as a yardstick to which all variables are compared. If a variable is less useful than random numbers for predicing the price, they are not very useful. 

```{r}
shrimp.data.RF <- RF.shrimp.data(shrimp.data)

M.1 <- as.formula("PRICE ~ SP_GROUP_f+
                       SIZE_GROUP_f +
                       SHRIMP_PROCESSING_f +
                       YEAR + ZIP_f + MARKETTYPE_f +
                       ECOLABEL_f + PROD_METHOD_f + RV")

#p <- length(attr(terms(M.1), "term.labels"))
# floor(sqrt(p)) and try half and 2x that
#mtry <- floor(sqrt(p)/2)
#mtry <- floor(sqrt(p))
  

```


The variable importance metric is the mean difference in MSEs between out-of-bag (OOB) predictions and those from one variable permuted. The mean is computed from all trees and the mean divided by the standard deviation of the differences. 

```{r}
if (!file.exists("RData/RF_M_1_out.rds")){
  RF.M.1 <- randomForest(formula = M.1,
                         data = shrimp.data.RF,
                         ntree = ntree,
                         localImp = TRUE,
                         immportance = FALSE,
                         proximity = FALSE,
                         do.trace = 500)
  
  saveRDS(RF.M.1, file = "RData/RF_M_1_out.rds")
  
} else {
  RF.M.1 <- readRDS("RData/RF_M_1_out.rds")
}
RF.M.1
```
About 67% of variability was explained by the forest, when PROD_METHOD was not included. It is 71% when PROD_METHOD is included. 

Now I start looking at which variables are influential in predicting the price using randomForestExplainer package. 
```{r}
if (!file.exists("RData/RF_M_1_min_depth.rds")){
  min_depth_df <- min_depth_distribution(RF.M.1)
  
  saveRDS(min_depth_df, file = "RData/RF_M_1_min_depth.rds")
} else {
  min_depth_df <- readRDS(file = "RData/RF_M_1_min_depth.rds")
}

plot_min_depth_distribution(min_depth_df)

# if there were missing values, can use the option mean_sample = "relevant_trees" in the above call.
```

Zip code is an important variable! 

More importance measures:
```{r}
if (!file.exists("RData/RF_M_1_importance.rds")){
  importance_df <- measure_importance(RF.M.1)
  
  saveRDS(importance_df, file = "RData/RF_M_1_importance.rds")
} else {
  importance_df <- readRDS("RData/RF_M_1_importance.rds")
}

plot_multi_way_importance(importance_df, 
                          size_measure = "no_of_nodes")
```

```{r}
plot_multi_way_importance(importance_df, 
                          x_measure = "mse_increase", 
                          y_measure = "node_purity_increase", 
                          size_measure = "p_value", 
                          no_of_labels = 5)
```


```{r}
# rearrange by increase in MSE in descending order (this result is hugely different from when randomForest::importance() is used... why is that? )

importance_df %>% mutate(var_name = case_when(variable == "SIZE_GROUP_f" ~ "SIZE",
                                                variable == "ZIP_f" ~ "ZIP",
                                                variable == "PROD_METHOD_f" ~ "WILD/FARM",
                                                variable == "MARKETTYPE_f" ~ "MARKET",
                                                variable == "SHRIMP_PROCESSING_f" ~ "PROCESSING",
                                                variable == "SP_GROUP_f" ~ "SPECIES",
                                                variable == "ECOLABEL_f" ~ "ECOLABEL",
                                                variable == "YEAR" ~ "YEAR",
                                                variable == "RV" ~ "RANDOM",
                                                TRUE ~ NA_character_)) -> var.imp.RF.df 

p.1 <- ggplot(data = var.imp.RF.df) + 
  geom_point(aes(x = mse_increase, 
                 y = reorder(var_name, mse_increase)),
             size = 3) + 
  theme_bw() + 
  labs(x = "Variable importance") + 
  theme(axis.title.y = element_blank(),
        axis.title.x = element_text(size =12))

ggsave(p.1, 
       filename = "figures/varImp_RF.png", 
       device = "png", dpi = 600)
print(p.1)

```

Size and zip turned out to be pretty important.  The result is quite different in scale when imporatance in randomForest is used...because using randomForest::importance will divide the mse_increase values by their SDs. 

```{r}
var.imp.df <- data.frame(importance(RF.M.1))
var.imp.df$variable <- rownames(var.imp.df) 
rownames(var.imp.df) <- NULL

var.imp.df %>% mutate(var_name = case_when(variable == "SIZE_GROUP_f" ~ "SIZE",
                                           variable == "ZIP_f" ~ "ZIP",
                                           variable == "PROD_METHOD_f" ~ "WILD/FARM",
                                           variable == "MARKETTYPE_f" ~ "MARKET",
                                           variable == "SHRIMP_PROCESSING_f" ~ "PROCESSING",
                                           variable == "SP_GROUP_f" ~ "SPECIES",
                                           variable == "ECOLABEL_f" ~ "ECOLABEL",
                                           variable == "YEAR" ~ "YEAR",
                                           variable == "RV" ~ "RANDOM",
                                           TRUE ~ NA_character_)) -> var.imp.df

p.1a <- ggplot(data = var.imp.df) + 
  geom_point(aes(x = X.IncMSE, 
                 y = reorder(var_name, X.IncMSE)),
             size = 3) + 
  theme_bw() + 
  labs(x = "Variable importance") + 
  theme(axis.title.y = element_blank(),
        axis.title.x = element_text(size =12))

ggsave(p.1a, 
       filename = "figures/varImp_RFa.png", 
       device = "png", dpi = 600)
print(p.1a)
```



```{r}

pred.RF.M.1 <- predict(RF.M.1)
shrimp.data.RF$PREDICT <- pred.RF.M.1
p.2 <- ggplot(data = shrimp.data.RF) + 
  geom_point(aes(x = PRICE, y = PREDICT)) + 
  geom_abline(slope = 1, intercept = 0,
              size = 1.2) + 
  labs(x = "Observed price ($/lb)", y = "Predicted price ($/lb)")

ggsave(p.2, 
       filename = "figures/ObsVsPred_RF.png", 
       device = "png", dpi = 600)
print(p.2)
```



rfPermute takes waaaaay too long to compute. Results are saved in a file. 
```{r}

if (!file.exists("RData/RFpermute_M_1.rds")){
  var.imp.rfPermute <- rfPermute(formula = M.1,
                                 data = shrimp.data.RF,
                                 ntree = ntree)
  #,num.cores = 1
  saveRDS(var.imp.rfPermute, file = "RData/RFpermute_M_1.rds")
} else {
  var.imp.rfPermute <- readRDS(file = "RData/RFpermute_M_1.rds")

}
# 
#p1 <- plot(rp.importance(var.imp.rfPermute, scale = F))
# "scaling" will divide change in MSEs by SDs - same as using randomForest::varImp, when scale = T,
# same as randomForestExplainer::measure_importance()
p2 <- plot(rp.importance(var.imp.rfPermute, scale = T))
 
```

Again, SIZE_GROUP and ZIP are the two major contributors.  

Let's look at interactions using randomForestExplainer functions.

```{r}
int.vars <- important_variables(importance_df, 
                                k = 4, 
                                measures = c("mean_min_depth", "no_of_trees"))

if (!file.exists("RData/RF_M_1_interactions.rds")){
  interactions.df <- min_depth_interactions(RF.M.1, int.vars)
  saveRDS(interactions.df, "RData/RF_M_1_interactions.rds")
  
} else {
  interactions.df <- readRDS("RData/RF_M_1_interactions.rds")
}

plot_min_depth_interactions(interactions.df)

```

The following does the same things as above - so it takes a loooong time to complete. Don't. 
```{r}

#explain_forest(RF.M.1, interactions = TRUE, data = shrimp.data.RF)
```

